
\documentclass[fleqn,leqno,11pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amssymb}
\usepackage{econ}

%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2953}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{Created=Tue Feb 10 10:33:10 1998}
%TCIDATA{LastRevised=Monday, December 18, 2006 11:28:06}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}
%TCIDATA{CSTFile=Econ.cst}

\input{tcilatex}
\renewenvironment{description}
                {\list{}{\listparindent -\parindent
                  \let\makelabel\descriptionlabel
                  \itemsep       8pt
                  \parsep        0pt
                        \itemindent    \listparindent
                        \leftmargin    \parindent}}
                {\endlist}
\input{lefttag.sty}
\setstretch{1.48}
\setlength{\topmargin}{.3in}
\setlength{\oddsidemargin}{.75in}
\setlength{\evensidemargin}{.75in}
\setlength{\textwidth}{6.9in}
\setlength{\textheight}{9.05in}
\setlength{\footskip}{0.4in}
\setlength{\parindent}{0.4in}
\setcounter{page}{1}
\font\smcaps=cmcsc10

\begin{document}

\title{BUSINESS CYCLE ACCOUNTING}
\author{V. V. Chari, Patrick J. Kehoe, and Ellen R. McGrattan\thanks{%
We thank the co-editor and three referees for useful comments. We also thank
Kathy Rolfe for excellent editorial assistance and the National Science
Foundation for financial support. The views expressed herein are those of
the authors and not necessarily those of the Federal Reserve Bank of
Minneapolis or the Federal Reserve System.}}
\maketitle

\begin{abstract}
We propose a simple method to help researchers develop quantitative models
of economic fluctuations. The method rests on the insight that many models
are equivalent to a prototype growth model with time-varying wedges which
resemble productivity, labor and investment taxes, and government
consumption. Wedges corresponding to these variables---\textit{efficiency}, 
\textit{labor}, \textit{investment,} and \textit{government consumption
wedges}---are measured and then fed back into the model in order to assess
the fraction of various fluctuations they account for. Applying this method
to U.S. data for the Great Depression and the 1982 recession reveals that
the efficiency and labor wedges together account for essentially all of the
fluctuations; the investment wedge plays a decidedly tertiary role, and the
government consumption wedge, none. Analyses of the entire postwar period
and alternative model specifications support these results. Models with
frictions manifested primarily as investment wedges are thus not promising
for the study of business cycles.\newline
\end{abstract}

\noindent In building detailed, quantitative models of economic
fluctuations, researchers face hard choices about where to introduce
frictions into their models in order to allow the models to generate
business cycle fluctuations similar to those in the data. Here we propose a
simple method to guide these choices, and we demonstrate how to use it.

Our method has two components: an equivalence result and an accounting
procedure. The \textit{equivalence result} is that a large class of models,
including models with various types of frictions, are equivalent to a
prototype model with various types of time-varying wedges that distort the
equilibrium decisions of agents operating in otherwise competitive markets.
At face value, these wedges look like time-varying productivity, labor
income taxes, investment taxes, and government consumption. We thus label
the wedges \textit{efficiency wedges}, \textit{labor wedges}, \textit{%
investment wedges}, and \textit{government consumption wedges}.

The \textit{accounting procedure} also has two components. It begins by
measuring the wedges, using data together with the equilibrium conditions of
a prototype model. The measured wedge values are then fed back into the
prototype model, one at a time and in combinations, in order to assess how
much of the observed movements of output, labor, and investment can be
attributed to each wedge, separately and in combinations. By construction,
all four wedges account for all of these observed movements. This accounting
procedure leads us to label our method \textit{business cycle accounting}.

To demonstrate how the accounting procedure works, we apply it to two actual
U.S. business cycle episodes: the most extreme in U.S. history, the Great
Depression (1929--39), and a downturn less severe and more like those seen
since World War II, the 1982 recession. For the Great Depression period, we
find that, in combination, the efficiency and labor wedges produce declines
in output, labor, and investment from 1929 to 1933 only slightly more severe
than in the data. These two wedges also account fairly well for the behavior
of those variables in the recovery. Over the entire Depression period,
however, the investment wedge actually drives output the wrong way, leading
to an increase in output during much of the 1930s. Thus, the investment
wedge cannot account for either the long, deep downturn or the subsequent
slow recovery. Our analysis of the more typical 1982 U.S. recession produces
essentially the same results for the efficiency and labor wedges in
combination. Here the investment wedge plays essentially no role. In both
episodes, the government consumption wedge plays virtually no role.

We extend our analysis to the entire postwar period by developing some
summary statistics for 1959--2004. The statistics we focus on are the output
fluctuations induced by each wedge alone and the correlations between those
fluctuations and those actually in the data. Our findings from these
statistics suggest that over the entire postwar period the investment wedge
plays a somewhat larger role in business cycle fluctuations than in the 1982
recession, but its role is substantially smaller than that of either the
labor or efficiency wedges.

We begin our demonstration of our proposed method by establishing
equivalence results that link the four wedges to detailed models. We start
with detailed model economies in which technologies and preferences are
similar to those in a benchmark prototype economy and show that frictions in
the detailed economies manifest themselves as wedges in the prototype
economy. We show that an economy in which the technology is constant but
input-financing frictions vary over time is equivalent to a growth model
with efficiency wedges. We show that an economy with sticky wages and
monetary shocks, like that of Bordo, Erceg, and Evans (2000), is equivalent
to a growth model with labor wedges. In the appendix, we show that an
economy with the type of credit market frictions considered by those of
Bernanke, Gertler, and Gilchrist (1999) is equivalent to a growth model with
investment wedges. Also in the appendix, we show that an open economy model
with fluctuating borrowing and lending is equivalent to a prototype
(closed-economy) model with government consumption wedges. In the working
paper version of this paper (Chari, Kehoe, and McGrattan (2004)), we also
show that an economy with the type of credit market frictions considered by
Carlstrom and Fuerst (1997) is equivalent to a growth model with investment
wedges and that an economy with unions and antitrust policy shocks, like
that of Cole and Ohanian (2004), is equivalent to a growth model with labor
wedges.

Similar equivalence results can be established when technology and
preferences in detailed economies are very different from those in the
prototype economy. In such situations, the prototype economy can have wedges
even if the detailed economies have no frictions. We show how wedges in the
benchmark prototype economy can be decomposed into a part due to frictions
and a part due to differences in technology and preferences by constructing
alternative prototype economies which have technologies and preferences
similar to those in the detailed economy.

Our quantitative findings suggest that financial frictions which manifest
themselves primarily as investment wedges do not play a primary role in the
Great Depression or postwar recessions. Such financial frictions play a
prominent role in the models of Bernanke and Gertler (1989), Carlstrom and
Fuerst (1997), Kiyotaki and Moore (1997), and Bernanke, Gertler, and
Gilchrist (1999). More promising, our findings suggest, are models in which
the underlying frictions manifest themselves as efficiency and labor wedges.
One such model is the input-financing friction model described here in which
financial frictions manifest themselves primarily as efficiency wedges. This
model is consistent with the views of Bernanke (1983) on the importance of
financial frictions. Also promising are sticky wage models with monetary
shocks, such as that of Bordo, Erceg, and Evans (2000), and models with
monopoly power, such as that of Cole and Ohanian (2004) in which the
underlying frictions manifest themselves primarily as labor wedges. In
general, this application of our method suggests that successful future work
will likely include mechanisms in which efficiency and labor wedges have a
primary role and the investment wedge has, at best, a tertiary role. We view
this finding as our key substantive contribution.

In our quantitative work, we also analyze some detailed economies with quite
different technology and preferences than those in our benchmark prototype
economy. These include variable instead of fixed capital utilization,
different labor supply elasticities, and costs of adjusting investment. For
these alternative detailed economies, we decompose the benchmark prototype
wedges into their two sources, frictions and specification differences, by
constructing alternative prototype economies that are equivalent to the
detailed economies and so can measure the part of the wedges due to
frictions. We find that with regard to the investment wedge's role in the
business cycle, frictions driving that wedge are unchanged by different
labor supply elasticities and worsened by variable capital
utilization---with the latter specification, for example, the investment
wedge boosts output even more during the Great Depression than it did in the
benchmark economy. With investment adjustment costs, the frictions driving
investment wedges do at least depress output during the downturns, but only
modestly. Altogether, these analyses reinforce our conclusion that the
investment wedge plays a decidedly tertiary role in business cycle
fluctuations.

Our business cycle accounting method is intended to shed light on promising
classes of mechanisms through which primitive shocks lead to economic
fluctuations. It is not intended to identify the primitive sources of
shocks. Many economists think, for example, that monetary shocks drove the
U.S. Great Depression, but these economists disagree about the details of
the driving mechanism. Our analysis suggests that models in which financial
frictions show up primarily as investment wedges are not promising while
models in which financial frictions show up as efficiency or labor wedges
may well be. Thus, we conclude that researchers interested in developing
models in which monetary shocks lead to the Great Depression should focus on
detailed models in which financial frictions manifest themselves as
efficiency and labor wedges.

Other economists, including Cole and Ohanian (1999 and 2004) and Prescott
(1999), emphasize nonmonetary factors behind the Great Depression,
downplaying the importance of money and banking shocks. For such economists,
our analysis guides them to promising models, like that of Cole and Ohanian
(2004), in which fluctuations in the power of unions and cartels lead to
labor wedges, and other models in which poor government policies lead to
efficiency wedges.

In terms of method, the equivalence result provides the logical foundation
for the way our accounting procedure uses the measured wedges. At a
mechanical level, the wedges represent deviations in the prototype model's
first-order conditions and in its relationship between inputs and outputs.
One interpretation of these deviations, of course, is that they are simply
errors, so that their size indicates the goodness-of-fit of the model. Under
that interpretation, however, feeding the measured wedges back into the
model makes no sense. Our equivalence result leads to a more economically
useful interpretation of the deviations by linking them directly to classes
of models; that link provides the rationale for feeding the measured wedges
back into the model.

Also in terms of method, the accounting procedure goes beyond simply
plotting the wedges. Such plots, by themselves, are not useful in evaluating
the quantitative importance of competing mechanisms of business cycles
because they tell us little about the equilibrium responses to the wedges.
Feeding the measured wedges back into the prototype model and measuring the
model's resulting equilibrium responses is what allows us to discriminate
between competing mechanisms.

Finally, in terms of method, our decomposition of business cycle
fluctuations is quite different from traditional decompositions. Those
decompositions attempt to isolate the effects of (so-called) primitive
shocks on equilibrium outcomes by making identifying assumptions, typically
zero-one restrictions on variables and shocks. The problem with the
traditional approach is that finding identifying assumptions that apply to a
broad class of detailed models is hard. Hence, this approach is not useful
in pointing researchers toward classes of promising models. Our approach, in
contrast, can be applied to a broad class of detailed models. Our
equivalence results, which provide a mapping from wedges to frictions in
particular detailed models, play the role of the identifying assumptions in
the traditional approach. This mapping is detailed-model specific and is the
key to interpreting the properties of the wedges we document. For any
detailed model of interest, researchers can use the mapping that is relevant
for their model to learn whether it is promising. In this sense our
approach, while being purposefully less ambitious than the traditional
approach, is much more flexible than that approach.

Our accounting procedure is intended to be a useful first step in guiding
the construction of detailed models with various frictions, to help
researchers decide which frictions are quantitatively important to business
cycle fluctuations. The procedure is not a way to test particular detailed
models. If a detailed model is at hand, then it makes sense to confront that
model directly with the data. Nevertheless, our procedure is useful in
analyzing models with many frictions. For example, some researchers, such as
Bernanke, Gertler, and Gilchrist (1999) and Christiano, Gust, and Roldos
(2004), have argued that the data are well accounted for by models which
include a host of frictions (such as credit market frictions, sticky wages,
and sticky prices). Our analysis suggests that the features of these models
which primarily lead to investment wedges can be dropped while only modestly
affecting the models' ability to account for the data.

Our work here is related to a vast business cycle literature that we discuss
in detail after we describe and apply our new method.

\bigskip

\begin{center}
1. \textsc{Demonstrating the Equivalence Result}
\end{center}

Here we show how various detailed models with underlying distortions are
equivalent to a prototype growth model with one or more wedges.

\bigskip

\begin{center}
1.1. \emph{The Benchmark Prototype Economy}
\end{center}

The \emph{benchmark }prototype economy that we use later in our accounting
procedure is a stochastic growth model. In each period $t,$ the economy
experiences one of finitely many events $s_{t},$ which index the shocks. We
denote by $s^{t}=(s_{0},...,s_{t})$ the history of events up through and
including period $t$ and often refer to $s^{t}$ as the \textit{state}. The
probability, as of period $0$, of any particular history $s^{t}$ is $\pi
_{t}(s^{t})$. The initial realization $s_{0}$ is given. The economy has four
exogenous stochastic variables, all of which are functions of the underlying
random variable $s^{t}$: the \textit{efficiency wedge }$A_{t}(s^{t}),$ the 
\textit{labor wedge }$1-\tau _{lt}(s^{t}),$ the \textit{investment wedge} $%
1/[1+\tau _{xt}(s^{t})]$, and the \textit{government consumption wedge }$%
g_{t}(s^{t})$.

In the model, consumers maximize expected utility over per capita
consumption $c_{t}$ and per capita labor $l_{t}$, 
\[
\sum_{t=0}^{\infty }\sum_{s^{t}}\beta ^{t}\pi _{t}(s^{t})U\text{{\large (}}%
c_{t}(s^{t}),l_{t}(s^{t})\text{{\large )}}N_{t}, 
\]%
subject to the budget constraint 
\[
c_{t}+[1+\tau _{xt}(s^{t})]x_{t}(s^{t})=[1-\tau
_{lt}(s^{t})]w_{t}(s^{t})l_{t}(s^{t})+r_{t}(s^{t})k_{t}(s^{t-1})+T_{t}(s^{t}) 
\]%
and the capital accumulation law 
\begin{equation}
(1+\gamma _{n})k_{t+1}(s^{t})=(1-\delta )k_{t}(s^{t-1})+x_{t}(s^{t}),
\label{1}
\end{equation}%
where $k_{t}(s^{t-1})$ denotes the per capita capital stock, $x_{t}(s^{t})$
per capita investment, $w_{t}(s^{t})$ the wage rate, $r_{t}(s^{t})$ the
rental rate on capital, $\beta $ the discount factor, $\delta $ the
depreciation rate of capital, $N_{t}$ the population with growth rate equal
to $1+\gamma _{n}$, and $T_{t}(s^{t})$ per capita lump-sum transfers.

The production function is $F${\large (}$k_{t}(s^{t-1}),(1+\gamma
)^{t}l_{t}(s^{t})${\large )}, where $1+\gamma $ is the rate of
labor-augmenting technical progress, which is assumed to be a constant.
Firms maximize profits given by $A_{t}(s^{t})F${\large (}$%
k_{t}(s^{t-1}),(1+\gamma )^{t}l_{t}(s^{t})${\large )}$%
-r_{t}(s^{t})k_{t}(s^{t-1})-w_{t}(s^{t})l_{t}(s^{t})$.

The equilibrium of this benchmark prototype economy is summarized by the
resource constraint, 
\begin{equation}
c_{t}(s^{t})+x_{t}(s^{t})+g_{t}(s^{t})=y_{t}(s^{t}),  \label{resource}
\end{equation}%
where $y_{t}(s^{t})$\ denotes per capita output, together with 
\begin{equation}
y_{t}(s^{t})=A_{t}(s^{t})F\text{{\large (}}k_{t}(s^{t-1}),(1+\gamma
)^{t}l_{t}(s^{t})\text{{\large )}},  \label{AA}
\end{equation}%
\begin{equation}
-\frac{U_{lt}(s^{t})}{U_{ct}(s^{t})}=[1-\tau
_{lt}(s^{t})]A_{t}(s^{t})(1+\gamma )^{t}F_{lt},\text{ and }  \label{taun}
\end{equation}%
\begin{equation}
U_{ct}(s^{t})[1+\tau _{xt}(s^{t})]  \label{taux}
\end{equation}%
\[
=\beta \sum_{s^{t+1}}\pi
_{t}(s^{t+1}|s^{t})U_{ct+1}(s^{t+1})\{A_{t+1}(s^{t+1})F_{kt+1}(s^{t+1})+(1-%
\delta )[1+\tau _{xt+1}(s^{t+1})]\}, 
\]%
where, here and throughout, notations like $U_{ct}$, $U_{lt}$, $F_{lt}$, and 
$F_{kt}$ denote the derivatives of the utility function and the production
function with respect to their arguments and $\pi _{t}(s^{t+1}|s^{t})$
denotes the conditional probability $\pi _{t}(s^{t+1})/\pi _{t}(s^{t})$. We
assume that $g_{t}(s^{t})$ fluctuates around a trend of $(1+\gamma )^{t}.$

Notice that in this benchmark prototype economy, the efficiency wedge
resembles a blueprint technology parameter, and the labor wedge and the
investment wedge resemble tax rates on labor income and investment. Other
more elaborate models could be considered, models with other kinds of
frictions that look like taxes on consumption or on capital income.
Consumption taxes induce a wedge between the consumption-leisure marginal
rate of substitution and the marginal product of labor in the same way as do
labor income taxes. Such taxes, if time-varying, also distort the
intertemporal margins in (\ref{taux}). Capital income taxes induce a wedge
between the intertemporal marginal rate of substitution and the marginal
product of capital which is only slightly different from the distortion
induced by a tax on investment. We experimented with intertemporal
distortions that resemble capital income taxes rather than investment taxes
and found that our substantive conclusions are unaffected. (For details, see
Chari, Kehoe, and McGrattan (2006), hereafter referred to as the \emph{%
technical appendix}.)

We emphasize that each of the wedges represents the overall distortion to
the relevant equilibrium condition of the model. For example, distortions
both to labor supply affecting consumers and to labor demand affecting firms
distort the static first-order condition (\ref{taun}). Our labor wedge
represents the sum of these distortions. Thus, our method identifies the
overall wedge induced by both distortions and does not identify each
separately. Likewise, liquidity constraints on consumers distort the
consumer's intertemporal Euler equation, while investment financing
frictions on firms distort the firm's intertemporal Euler equation. Our
method combines the Euler equations for the consumer and the firm and
therefore identifies only the overall wedge in the combined Euler equation
given by (\ref{taux}). We focus on the overall wedges because what matters
in determining business cycle fluctuations is the overall wedges, not each
distortion separately.

\bigskip

\begin{center}
1.2. \emph{The Mapping---From Frictions to Wedges}
\end{center}

Now we illustrate the mapping between detailed economies and prototype
economies for two types of wedges. We show that input-financing frictions in
a detailed economy map into efficiency wedges in our prototype economy.
Sticky wages in a monetary economy map into our prototype (real) economy
with labor wedges. In an appendix, we show as well that investment-financing
frictions map into investment wedges and that fluctuations in net exports in
an open economy map into government consumption wedges in our prototype
(closed) economy. In general, our approach is to show that the frictions
associated with specific economic environments manifest themselves as
distortions in first-order conditions and resource constraints in a growth
model. We refer to these distortions as \emph{wedges}.

We choose simple models in order to illustrate how the detailed models map
into the prototypes. Since many models map into the same configuration of
wedges, identifying one particular configuration does not uniquely identify
a model; rather, it identifies a whole class of models consistent with that
configuration. In this sense, our method does not uniquely determine the
model most promising to analyze business cycle fluctuations. It does,
however, guide researchers to focus on the key margins that need to be
distorted in order to capture the nature of the fluctuations.

\bigskip \newpage

\noindent a. \emph{Efficiency Wedges}

In many economies, underlying frictions either within or across firms cause
factor inputs to be used inefficiently. These frictions in an underlying
economy often show up as aggregate productivity shocks in a prototype
economy similar to our benchmark economy. Schmitz (2005) presents an
interesting example of within-firm frictions resulting from work rules that
lower measured productivity at the firm level. Lagos (2006) studies how
labor market policies lead to misallocations of labor across firms and,
thus, to lower aggregate productivity. And Chu (2001) and Restuccia and
Rogerson (2003) show how government policies at the levels of plants and
establishments lead to lower aggregate productivity.

Here we develop a detailed economy with input-financing frictions and use it
to make two points. This economy illustrates the general idea that frictions
which lead to inefficient factor utilization map into efficiency wedges in a
prototype economy. Beyond that, however, the economy also demonstrates that
financial frictions can show up as efficiency wedges rather than as
investment wedges. In our detailed economy, financing frictions lead some
firms to pay higher interest rates for working capital than do other firms.
Thus, these frictions lead to an inefficient allocation of inputs across
firms.

\bigskip

\noindent $\square $ \emph{A Detailed Economy With Input-Financing Frictions}

Consider a simple detailed economy with financing frictions which distort
the allocation of intermediate inputs across two types of firms. Both types
of firms must borrow to pay for an intermediate input in advance of
production. One type of firm is more financially constrained, in the sense
that it pays a higher interest rate on borrowing than does the other type.
We think of these frictions as capturing the idea that some firms, such as
small firms, often have difficulty borrowing. One motivation for the higher
interest rate faced by the financially constrained firms is that moral
hazard problems are more severe for small firms.

Specifically, consider the following economy. Aggregate gross output $q_{t}$
is a combination of the gross output $q_{it}$ from the economy's two
sectors, indexed $i=1,2$, where 1 indicates the sector of firms that are
more financially constrained and 2 the sector of firms that are less
financially constrained. The sectors' gross output is combined\ according to 
\begin{equation}
q_{t}=q_{1t}^{\phi }q_{2t}^{1-\phi },  \label{q}
\end{equation}
where $0<\phi <1.$ The representative producer of the gross output $q_{t}$
chooses $q_{1t}$ and $q_{2t}$ to solve this problem: 
\[
\max \ q_{t}-p_{1t}q_{1t}-p_{2t}q_{2t} 
\]
subject to (\ref{q}), where $p_{it}$ is the price of the output of sector $i$%
.

The resource constraint for gross output in this economy is 
\begin{equation}
c_{t}+k_{t+1}+m_{1t}+m_{2t}=q_{t}+(1-\delta )k_{t},  \label{gross output}
\end{equation}
where $c_{t}$ is consumption, $k_{t}$ is the capital stock, and $m_{1t}$ and 
$m_{2t}$ are intermediate goods used in sectors 1 and 2, respectively. Final
output, given by $y_{t}=$ $q_{t}-$ $m_{1t}-$ $m_{2t}$, is gross output less
the intermediate goods used.

The gross output of each sector $i$, $q_{it}$, is made from intermediate
goods $m_{it}$ and a composite value-added good $z_{it}$ according to 
\begin{equation}
q_{it}=m_{it}^{\theta }z_{it}^{1-\theta },  \label{stupid}
\end{equation}
where $0<\theta <1.$ The composite value-added good is produced from capital 
$k_{t}$ and labor $l_{t}$ according to 
\begin{equation}
z_{1t}+z_{2t}=z_{t}=F(k_{t},l_{t}).  \label{z}
\end{equation}

The producer of gross output of sector $i$ chooses the composite good $%
z_{it} $ and the intermediate good $m_{it}$ to solve this problem: 
\[
\max \ p_{it}q_{it}-v_{t}z_{it}-R_{it}m_{it} 
\]
subject to (\ref{stupid}). Here $v_{t}$ is the price of the composite good
and $R_{it}$ is the gross within-period interest rate paid on borrowing by
firms in sector $i.$ If firms in sector $1$ are more financially constrained
than those in sector 2, then $R_{1t}>R_{2t}.$ Let $R_{it}=R_{t}(1+\tau
_{it}) $, where $R_{t}$ is the rate consumers earn within period $t$ and $%
\tau _{it} $ measures the within-period spread, induced by financing
constraints, between the rate paid to consumers who save and the rate paid
by firms in sector $i$. Since consumers do not discount utility within the
period, $R_{t}=1.$

In this economy, the representative producer of the composite good $z_{t}$
chooses $k_{t}$ and $l_{t}$ to solve this problem: 
\[
\max \ v_{t}z_{t}-w_{t}l_{t}-r_{t}k_{t} 
\]
subject to (\ref{z}), where $w_{t}$ is the wage rate and $r_{t}$ is the
rental rate on capital.

Consumers solve this problem: 
\begin{equation}
\max \ \sum_{t=0}^{\infty }\beta ^{t}U(c_{t},l_{t})  \label{consumer}
\end{equation}%
subject to 
\[
c_{t}+k_{t+1}=r_{t}k_{t}+w_{t}l_{t}+(1-\delta )k_{t}+T_{t}, 
\]%
where $l_{t}=l_{1t}+l_{2t}$ is the economy's total labor supply and $%
T_{t}=R_{t}\sum_{i}\tau _{it}m_{it}$ lump-sum transfers. Here we assume that
the financing frictions act like distorting taxes, and the proceeds are
rebated to consumers. If, instead, we assumed that these frictions
represent, say, lost gross output, then we would adjust the economy's
resource constraint (\ref{gross output}) appropriately.

\bigskip

\noindent $\square $ \emph{The Associated Prototype Economy With Efficiency
Wedges}

Now consider a version of the benchmark prototype economy that will have the
same aggregate allocations as the input-financing frictions economy just
detailed. This prototype economy is identical to our benchmark prototype
except that the new prototype economy has an investment wedge that resembles
a tax on capital income rather than a tax on investment. Here the government
consumption wedge is set equal to zero.

Now the consumer's budget constraint is 
\begin{equation}
c_{t}+k_{t+1}=(1-\tau _{kt})r_{t}k_{t}+(1-\tau _{lt})w_{t}l_{t}+(1-\delta
)k_{t}+T_{t},  \label{budget A}
\end{equation}
and the efficiency wedge is 
\begin{equation}
A_{t}=\kappa (a_{1t}^{1-\phi }a_{2t}^{\phi })^{\frac{\theta }{1-\theta }%
}[1-\theta (a_{1t}+a_{2t})],  \label{Ainput}
\end{equation}
where $a_{1t}=\phi /(1+\tau _{1t})$, $a_{2t}=(1-\phi )/(1+\tau _{2t}),$ $%
\kappa =[\phi ^{\phi }(1-\phi )^{1-\phi }\theta ^{\theta }]^{\frac{1}{%
1-\theta }},$ and $\tau _{1t}$ and $\tau _{2t}$ are the interest rate
spreads in the detailed economy.

Comparing the first-order conditions in the detailed economy with
input-financing frictions to those of the associated prototype economy with
efficiency wedges leads immediately to this proposition: \bigskip

\textsc{Proposition }1:\textit{\ }\emph{Consider the prototype economy with
resource constraint} (\ref{resource}) \emph{and consumer budget constraint} (%
\ref{budget A}) \emph{with exogenous processes for the efficiency wedge }$%
A_{t}$\emph{\ given in }(\ref{Ainput}), \emph{the labor wedge given by } 
\begin{equation}
\frac{1}{1-\tau _{lt}}=\frac{1}{1-\theta }\left[ 1-\theta \left( \frac{\phi 
}{1+\tau _{1t}^{\ast }}+\frac{1-\phi }{1+\tau _{2t}^{\ast }}\right) \right] ,
\label{tax}
\end{equation}
\emph{and the investment wedge given by} $\tau _{kt}=\tau _{lt}$\emph{,} 
\emph{where} $\tau _{1t}^{\ast }$ \emph{and} $\tau _{2t}^{\ast }$ \emph{are
the interest rate spreads from the detailed economy with input-financing
frictions. Then the equilibrium allocations for aggregate variables in the
detailed economy are equilibrium allocations in this prototype economy.}%
\bigskip

Consider the following special case of Proposition 1 in which only the
efficiency wedge fluctuates. Specifically, suppose that in the detailed
economy the interest rate spreads $\tau _{1t}$ and $\tau _{2t}$ fluctuate
over time, but in such a way that the weighted average of these spreads, 
\begin{equation}
a_{1t}+a_{2t}=\frac{\phi }{1+\tau _{1t}}+\frac{1-\phi }{1+\tau _{2t}},
\label{average wedge}
\end{equation}
is constant while $a_{1t}^{1-\phi }a_{2t}^{\phi }$ fluctuates. Then from (%
\ref{tax}) we see that the labor and investment wedges are constant, and
from (\ref{Ainput}) we see that the efficiency wedge fluctuates. In this
case, on average, financing frictions are unchanged, but relative
distortions fluctuate. An outside observer who attempted to fit the data
generated by the detailed economy with input-financing frictions to the
prototype economy would identify the fluctuations in relative distortions
with fluctuations in technology and would see no fluctuations in either the
labor wedge $1-\tau _{lt}$ or the investment wedge $\tau _{kt}$. In
particular, periods in which the relative distortions increase would be
misinterpreted as periods of technological regress.

\bigskip

\noindent b. \emph{Labor Wedges}

Now we show that a monetary economy with sticky wages is equivalent to a
(real) prototype economy with labor wedges. In the detailed economy, the
shocks are to monetary policy, while in the prototype economy, the shocks
are to the labor wedge.

\bigskip

\noindent $\square $ \emph{A Detailed Economy With Sticky Wages}

Consider a monetary economy populated by a large number of identical,
infinitely lived consumers. The economy consists of a competitive final
goods producer and a continuum of monopolistically competitive unions that
set their nominal wages in advance of the realization of shocks to the
economy. Each union represents all consumers who supply a specific type of
labor.

In each period $t,$ the commodities in this economy are a
consumption-capital good, money, and a continuum of differentiated types of
labor, indexed by $j$ $\in \lbrack 0,1]$. The technology for producing final
goods from capital and a labor aggregate at history, or state, $s^{t}$ has
constant returns to scale and is given by $y(s^{t})=F${\large (}$%
k(s^{t-1}),l(s^{t})${\large )}$,$ where $y(s^{t})$ is output of the final
good, $k(s^{t-1})$ is capital, and 
\begin{equation}
l(s^{t})=\left[ \int l(j,s^{t})^{v}\,dj\right] ^{\frac{1}{v}}  \label{labor}
\end{equation}
is an aggregate of the differentiated types of labor $l(j,s^{t})$.

The final goods producer in this economy behaves competitively. This
producer has some initial capital stock $k(s^{-1})$ and accumulates capital
according to $k(s^{t})=(1-\delta )k(s^{t-1})+x(s^{t})$, where $x(s^{t})$ is
investment. The present discounted value of profits for this producer is 
\begin{equation}
\ \sum_{t=0}^{\infty }\sum_{s^{t}}Q(s^{t})\left[
P(s^{t})y(s^{t})-P(s^{t})x(s^{t})-W(s^{t-1})l(s^{t})\right] ,
\label{profits}
\end{equation}
where $Q(s^{t})$ is the price of a dollar at $s^{t}$ in an abstract unit of
account, $P(s^{t})$ is the dollar price of final goods at $s^{t}$, and $%
W(s^{t-1})$ is the aggregate nominal wage at $s^{t}$ which depends on only $%
s^{t-1}$ because of wage stickiness.

The producer's problem can be stated in two parts. First, the producer
chooses sequences for capital $k(s^{t-1}),$ investment $x(s^{t}),$ and
aggregate labor $l(s^{t})$ in order to maximize (\ref{profits}) given the
production function and the capital accumulation law. The first-order
conditions can be summarized by 
\begin{equation}
P(s^{t})F_{l}(s^{t})=W(s^{t-1})\text{ and}  \label{foc 1}
\end{equation}
\begin{equation}
Q(s^{t})P(s^{t})=\sum_{s_{t+1}}Q(s^{t+1})P(s^{t+1})[F_{k}(s^{t+1})+1-\delta
].  \label{foc 2}
\end{equation}
Second, for any given amount of aggregate labor $l(s^{t}),$ the producer's
demand for each type of differentiated labor is given by the solution to

\begin{equation}
\min_{\{l(j,s^{t})\},j\in \lbrack 0,1]}\int \,W(j,s^{t-1})l(j,s^{t})\,dj
\label{wages}
\end{equation}
subject to (\ref{labor}); here $W(j,s^{t-1})$ is the nominal wage for
differentiated labor of type $j$. Nominal wages are set by unions before the
realization of the event in period $t$; thus, wages depend on, at most, $%
s^{t-1}.$ The demand for labor of type $j$ by the final goods producer is 
\begin{equation}
l^{d}(j,s^{t})=\left[ \frac{W(s^{t-1})}{W(j,s^{t-1})}\right] ^{\frac{1}{1-v}%
}l(s^{t}),  \label{labor demand}
\end{equation}
where $W(s^{t-1})\equiv \left[ \int \,W(j,s^{t-1})^{\frac{v}{v-1}}\,dj\right]
^{\frac{v-1}{v}}$ is the aggregate nominal wage. The minimized value in (\ref%
{wages}) is, thus, $W(s^{t-1})l(s^{t})$.

In this economy, consumers can be thought of as being organized into a
continuum of unions indexed by $j$. Each union consists of all the consumers
in the economy with labor of type $j$. Each union realizes that it faces a
downward-sloping demand for its type of labor, given by (\ref{labor demand}%
). In each period, the new wages are set before the realization of the
economy's current shocks.

The preferences of a representative consumer in the $j$th union is 
\begin{equation}
\sum_{t=0}^{\infty }\sum_{s^{t}}\,\beta ^{t}\pi _{t}(s^{t})\,\text{{\large [}%
}U\text{{\large (}}c(j,s^{t}),l(j,s^{t})\text{{\large )}}+V\text{{\large (}}%
M(j,s^{t})/P(s^{t})\text{{\large )]}},  \label{preferences}
\end{equation}%
where $c(j,s^{t}),l(j,s^{t}),M(j,s^{t})$ are the consumption, labor supply,
and money holdings of this consumer, and $P(s^{t})$ is the economy's overall
price level. Note that the utility function is separable in real balances.
This economy has complete markets for state-contingent nominal claims. The
asset structure is represented by a set of complete, contingent, one-period
nominal bonds. Let $B(j,s^{t+1})$ denote the consumers' holdings of such a
bond purchased in period $t$ at history $s^{t}$, with payoffs contingent on
some particular event $s_{t+1}$ in $t+1,$ where $s^{t+1}=(s^{t},s_{t+1})$.
One unit of this bond pays one dollar in period $t+1$ if the particular
event $s_{t+1}$ occurs and $0$ otherwise. Let $Q(s^{t+1}|s^{t})$ denote the
dollar price of this bond in period $t$ at history $s^{t}$, where $%
Q(s^{t+1}|s^{t})=Q(s^{t+1})/Q(s^{t}).$

The problem of the $j$th union is to maximize (\ref{preferences}) subject to
the budget constraint 
\begin{eqnarray*}
&&P(s^{t})c(j,s^{t})+M(j,s^{t})+\sum_{s_{t+1}}Q(s^{t+1}|s^{t})B(j,s^{t+1}) \\
&&\qquad \qquad \qquad \leq
W(j,s^{t-1})l(j,s^{t})+M(j,s^{t-1})+B(j,s^{t})+P(s^{t})T(s^{t})+D(s^{t}),
\end{eqnarray*}
the constraint $l(j,s^{t})=l^{d}(j,s^{t}),$ and the borrowing constraint $%
B(s^{t+1})\geq -P(s^{t})\overline{b}$, where $l^{d}(j,s^{t})$ is given by (%
\ref{labor demand})$.$ Here $T(s^{t})$ is transfers and the positive
constant $\overline{b}$ constrains the amount of real borrowing by the
union. Also, $D(s^{t})=$ $%
P(s^{t})y(s^{t})-P(s^{t})x(s^{t})-W(s^{t-1})l(s^{t})$ are the dividends paid
by the firms$.$ The initial conditions $M(j,s^{-1})$ and $B(j,s^{0})$ are
given and assumed to be the same for all $j.$ Notice that in this problem,
the union chooses the wage and agrees to supply whatever labor is demanded
at that wage.

The first-order conditions for this problem can be summarized by 
\begin{equation}
\frac{V_{m}(j,s^{t})}{P(s^{t})}-\frac{U_{c}(j,s^{t})}{P(s^{t})}+\beta
\sum_{s_{t+1}}\pi (s^{t+1}|s^{t})\frac{U_{c}(j,s^{t+1})}{P(s^{t+1})}=0,
\label{money foc}
\end{equation}%
\begin{equation}
Q(s^{t}|s^{t-1})=\beta \pi _{t}(s^{t}|s^{t-1})\frac{U_{c}(j,s^{t})}{%
U_{c}(j,s^{t-1})}\frac{P(s^{t-1})}{P(s^{t})}\text{, and }  \label{Q}
\end{equation}%
\begin{equation}
W(j,s^{t-1})=-\frac{%
\sum_{s^{t}}Q(s^{t})P(s^{t})U_{l}(j,s^{t})/U_{c}(j,s^{t})l^{d}(j,s^{t})}{%
v\sum_{s^{t}}Q(s^{t})l^{d}(j,s^{t})}.  \label{wage setting 1}
\end{equation}%
Here $\pi _{t}(s^{t+1}|s^{t})=$ $\pi _{t}(s^{t+1})/\pi _{t}(s^{t})$ is the
conditional probability of $s^{t+1}$ given $s^{t}$. Notice that in a steady
state, ($\ref{wage setting 1})$ reduces to $W/P=(1/v)(-U_{l}/U_{c}),$ so
that real wages are set as a markup over the marginal rate of substitution
between labor and consumption. Given the symmetry among the unions, all of
them choose the same consumption, labor, money balances, bond holdings, and
wages, which are denoted simply by $c(s^{t}),$ $l(s^{t}),$ $M(s^{t}),$ $%
B(s^{t+1})$, and $W(s^{t}).$

Consider next the specification of the money supply process and the
market-clearing conditions for this sticky-wage economy. The nominal money
supply process is given by $M(s^{t})=\mu (s^{t})M(s^{t-1})$, where $\mu
(s^{t})$ is a stochastic process. New money balances are distributed to
consumers in a lump-sum fashion by having nominal transfers satisfy $%
P(s^{t})T(s^{t})=M(s^{t})-M(s^{t-1})$. The resource constraint for this
economy is $c(s^{t})+k(s^{t})=y(s^{t})+(1-\delta )k(s^{t-1}).$ Bond
market--clearing requires that $B(s^{t+1})=0.$

\bigskip

\noindent $\square $ \emph{The Associated Prototype Economy With Labor Wedges%
}

Consider now a real prototype economy with labor wedges and the production
function for final goods given above in the detailed economy with sticky
wages$.$ The representative firm maximizes (\ref{profits}) subject to the
capital accumulation law given above. The first-order conditions can be
summarized by (\ref{foc 1}) and (\ref{foc 2}). The representative consumer
maximizes 
\[
\sum_{t=0}^{\infty }\sum_{s^{t}}\,\beta ^{t}\pi _{t}(s^{t})\,U\text{{\large (%
}}c(s^{t}),l(s^{t})\text{{\large )}} 
\]%
subject to the budget constraint 
\[
c(s^{t})+\sum_{s_{t+1}}q(s^{t+1}|s^{t})b(s^{t+1})\leq {\large [}1-\tau
_{l}(s^{t}){\large ]}w(s^{t})l(s^{t})+b(s^{t})+v(s^{t})+d(s^{t}) 
\]%
with $w(s^{t})$ replacing $W(s^{t-1})/P(s^{t})$ and $q(s^{t+1}/s^{t})$
replacing $Q(s^{t+1})P(^{st+1})/Q(s^{t})P(s^{t})$ and a bound on real bond
holdings, where the lowercase letters $q,b,w,v,$ and $d$ denote the real
values of bond prices, debt, wages, lump-sum transfers, and dividends. Here
the first-order condition for bonds is identical to that in (\ref{Q}) once
symmetry has been imposed with $q(s^{t}/s^{t-1})$ replacing $%
Q(s^{t}/s^{t-1})P(s^{t})/P(s^{t-1})$. The first-order condition for labor is
given by 
\[
-\frac{U_{l}(s^{t})}{U_{c}(s^{t})}={\large [}1-\tau _{l}(s^{t}){\large ]}%
w(s^{t}). 
\]

Consider an equilibrium of the sticky wage economy for some given stochastic
process $M^{\ast }(s^{t})$ on money supply. Denote all of the allocations
and prices in this equilibrium with asterisks. Then this proposition can be
easily established:

\bigskip

\textsc{Proposition} 2: \emph{Consider the prototype economy just described
with labor wedges given by } 
\begin{equation}
1-\tau _{l}(s^{t})=-\frac{U_{l}^{\ast }(s^{t})}{U_{c}^{\ast }(s^{t})}\frac{1%
}{F_{l}^{\ast }(s^{t})},  \label{labor wedge}
\end{equation}
\emph{where} $U_{l}^{\ast }(s^{t}),U_{c}^{\ast }(s^{t})$, \emph{and} $%
F_{l}^{\ast }(s^{t})$ \emph{are evaluated at the equilibrium of the sticky
wage economy and where real transfers are equal to the real value of
transfers in the sticky wage economy adjusted for the interest cost of
holding money. Then the equilibrium allocations and prices in the sticky
wage economy are the same as those in the prototype economy.}

\bigskip

The proof of this proposition is immediate from comparing the first-order
conditions, the budget constraints, and the resource constraints for the
prototype economy with labor wedges to those of the detailed economy with
sticky wages. The key idea is that distortions in the sticky-wage economy
between the marginal product of labor implicit in (\ref{wage setting 1}) and
the marginal rate of substitution between leisure and consumption are
perfectly captured by the labor wedges (\ref{labor wedge}) in the prototype
economy.

\bigskip \newpage

\begin{center}
2. \textsc{The Accounting Procedure}
\end{center}

Having established our equivalence result, we now describe our accounting
procedure at a conceptual level and discuss a Markovian implementation of it.

Our procedure is to conduct experiments that isolate the marginal effect of
each wedge as well as the marginal effects of combinations of these wedges
on aggregate variables. In the experiment in which we isolate the marginal
effect of the efficiency wedge, for example, we hold the other wedges fixed
at some constant values in all periods. In conducting this experiment, we
ensure that the probability distribution of the efficiency wedge coincides
with that in the prototype economy. In effect, we ensure that agents'
expectations of how the efficiency wedge will evolve are the same as in the
prototype economy. For each experiment, we compare the properties of the
resulting equilibria to those of the prototype economy. These comparisons,
together with our equivalence results, allow us to identify promising
classes of detailed economies.

\bigskip

\begin{center}
2.1 \emph{The Accounting Procedure at a Conceptual Level}
\end{center}

Suppose for now that the stochastic process $\pi _{t}(s^{t})$ and the
realizations of the state $s^{t}$ in some particular episode are known.
Recall that the prototype economy has one underlying (vector-valued) random
variable, the state $s^{t},$ which has a probability of $\pi _{t}(s^{t}).$
All of the other stochastic variables, including the four wedges---the
efficiency wedge $A_{t}(s^{t}),$ the labor wedge $1-\tau _{lt}(s^{t}),$ the
investment wedge $1/[1+\tau _{xt}(s^{t})]$, and the government consumption
wedge $g_{t}(s^{t})$---are simply functions of this random variable. Hence,
when the state $s^{t}$ is known, so are the wedges.

To evaluate the effects of just the efficiency wedge, for example, we
consider an economy, referred to as an \textit{efficiency wedge alone
economy,} with the same underlying state $s^{t}$ and probability $\pi
_{t}(s^{t})$ and the same function $A_{t}(s^{t})$ for the efficiency wedge
as in the prototype economy, but in which the other three wedges are set to
constants, in that $\tau _{lt}(s^{t})=\bar{\tau}_{l},\tau _{xt}(s^{t})=\bar{%
\tau}_{x},$ and $g_{t}(s^{t})=\bar{g}.$ Note that this construction ensures
that the probability distribution of the efficiency wedge in this economy is
identical to that in the prototype economy.

For the efficiency wedge alone economy, we then compute the equilibrium
outcomes associated with the realizations of the state $s^{t}$ in a
particular episode and compare these outcomes to those of the economy with
all four wedges. We find this comparison to be of particular interest
because in our applications, the realizations $s^{t}$ are such that the
economy with all four wedges exactly reproduces the data on output, labor,
investment, and consumption.

In a similar manner, we define the \textit{labor wedge alone economy}, the 
\textit{investment wedge alone economy}, and the \textit{government
consumption wedge alone economy, }as well as economies with a combination of
wedges such as the \textit{efficiency and labor wedge economy}.

\bigskip

\begin{center}
2.2 \emph{A Markovian Implementation}
\end{center}

So far we have described our procedure assuming that we know the stochastic
process $\pi _{t}(s^{t})$ and that we can observe the state $s^{t}.$ In
practice, of course, we need to either specify the stochastic process a
priori or use data to estimate it, and we need to uncover the state $s^{t}$
from the data. Here we describe a set of assumptions that makes these
efforts easy. Then we describe in detail the three steps involved in
implementing our procedure.

We assume that the state $s^{t}$ follows a Markov process of the form $\pi
(s_{t}|s_{t-1})$ and that the wedges in period $t$ can be used to uniquely
uncover the event $s_{t}$, in the sense that the mapping from the event $%
s_{t}$ to the wedges $(A_{t},\tau _{lt},\tau _{xt},g_{t})$ is one-to-one and
onto. Given this assumption, without loss of generality, let the underlying
event $s_{t}=(s_{At},s_{lt},s_{xt},s_{gt}),$ and let $A_{t}(s^{t})=s_{At},%
\tau _{lt}(s^{t})=s_{lt},\tau _{xt}(s^{t})=s_{xt},$ and $%
g_{t}(s^{t})=s_{gt}. $ Note that we have effectively assumed that agents use
only past wedges to forecast future wedges and that the wedges in period $t$
are sufficient statistics for the event in period $t.$

The first step in our procedure is to use data on $y_{t},l_{t},x_{t},$ and $%
g_{t}$ from an actual economy to estimate the parameters of the Markov
process $\pi (s_{t}|s_{t-1}).\ $We can do so using a variety of methods,
including the maximum likelihood procedure described below.

The second step in our procedure is to uncover the event $s_{t}$ by
measuring the realized wedges. We measure the government consumption wedge
directly from the data as the sum of government spending and net exports. To
obtain the values of the other three wedges, we use the data and the model's
decision rules. With $y_{t}^{d},l_{t}^{d},x_{t}^{d},g_{t}^{d}$, and $%
k_{0}^{d}$ denoting the data and $y(s_{t},k_{t}),\ l(s_{t},k_{t}),$ and$\
x(s_{t},k_{t})$ denoting the decision rules of the model, the realized wedge
series $s_{t}^{d}$ solves 
\begin{equation}
y_{t}^{d}=y(s_{t}^{d},k_{t}),~l_{t}^{d}=l(s_{t}^{d},k_{t}),\text{ and }%
x_{t}^{d}=x(s_{t}^{d},k_{t}),  \label{decision}
\end{equation}%
with $k_{t+1}=(1-\delta )k_{t}+x_{t}^{d},$ $k_{0}=k_{0}^{d}$, and $%
g_{t}=g_{t}^{d}.$ Note that we construct a series for the capital stock
using the capital accumulation law (\ref{1}), data on investment $x_{t}$,
and an initial choice of capital stock $k_{0}$. In effect, we solve for the
three unknown elements of the vector $s_{t}$ using the three equations (\ref%
{AA})--(\ref{taux}) and thereby uncover the state. We use the associated
values for the wedges in our experiments.

Note that the four wedges account for all of the movement in output, labor,
investment, and government consumption, in that if we feed the four wedges
into the three decision rules in (\ref{decision}) and use $%
g_{t}(s_{t}^{d})=s_{gt}\ $along with the law of motion for capital, we
simply recover the original data.

Note also that, in measuring the realized wedges, the estimated stochastic
process plays a role in measuring only the investment wedge. To see that the
stochastic process does not play a role in measuring the efficiency and
labor wedges, note that these wedges can equivalently be directly calculated
from (\ref{AA}) and (\ref{taun}) without computing the equilibrium of the
model. In contrast, calculating the investment wedge requires computing the
equilibrium of the model because the right side of (\ref{taux}) has
expectations over future values of consumption, the capital stock, the
wedges, and so on. The equilibrium of the model depends on these
expectations and, therefore, on the stochastic process driving the wedges.

The third step in our procedure is to conduct experiments to isolate the
marginal effects of the wedges. To do that, we allow a subset of the wedges
to fluctuate as they do in the data while the others are set to constants.
To evaluate the effects of the efficiency wedge, we compute the decision
rules for the efficiency wedge alone economy, denoted $%
y^{e}(s_{t},k_{t}),l^{e}(s_{t},k_{t}),$ and $x^{e}(s_{t},k_{t}),$ in which  $%
A_{t}(s^{t})=s_{At},\tau _{lt}(s^{t})=\bar{\tau}_{l},\tau _{xt}(s^{t})=\bar{%
\tau}_{x},$ and $g_{t}(s^{t})=\bar{g}.$ Starting from $k_{0}^{d}$, we then
use $s_{t}^{d}$, the decision rules, and the capital accumulation law to
compute the realized sequence of output, labor, and investment, $%
y_{t}^{e},l_{t}^{e},$ and $x_{t}^{e}$, which we call the \textit{efficiency
wedge components} of output, labor, and investment. We compare these
components to output, labor, and investment in the data. Other components
are computed and compared similarly.

Notice that in this experiment we computed the decision rules for an economy
in which only one wedge fluctuates and the others are set to be constants in
all events. The fluctuations in the one wedge are driven by fluctuations in
a 4 dimensional state $s_{t}.$

Notice also that our experiments are designed to separate out the direct
effect and the forecasting effect of fluctuations in wedges. As a wedge
fluctuates, it directly affects either budget constraints or resource
constraints. This fluctuation also affects the forecasts of that wedge as
well as of other wedges in the future. Our experiments are designed so that
when we hold a particular wedge constant, we eliminate the direct effect of
that wedge, but we retain its forecasting effect on the other wedges. By
doing so, we ensure that expectations of the fluctuating wedges are
identical to those in the prototype economy.

Here we focus on one simple way to specify the expectations of agents:
assume they simply use past values of the wedges to forecast future values.
An extension of our Markovian procedure is to use past endogenous variables,
such as output, investment, consumption, and perhaps even asset prices such
as stock market values, in addition to past wedges to forecast future
wedges. Another approach is to simply specify these expectations directly,
as we did in our earlier work (Chari, Kehoe, and McGrattan (2002)) and then
conduct a variety of experiments to determine how the results change as the
specification is changed.

\begin{center}
3. \textsc{Applying the Accounting Application}
\end{center}

Now we demonstrate how to apply our accounting procedure to two U.S.
business cycle episodes: the Great Depression and the postwar recession of
1982. We then extend our analysis to the entire postwar period. (In the
technical appendix, we describe in detail our data sources, parameter
choices, computational methods, and estimation procedures.)

\bigskip

\begin{center}
3.1. \emph{Details of the Application }
\end{center}

To apply our accounting procedure, we use functional forms and parameter
values familiar from the business cycle literature. We assume that the
production function has the form $F(k,l)=k^{\alpha }l^{1-\alpha }$ and the
utility function the form $U(c,l)=\log c+\psi \log (1-l).$ We choose the
capital share $\alpha =.35$ and the time allocation parameter $\psi =2.24.$
We choose the depreciation rate $\delta $, the discount factor $\beta $, and
growth rates $\gamma $ and $\gamma _{n}$\ so that, on an annualized basis,
depreciation is 4.64\%, the rate of time preference 3\%, the population
growth rate 1.5\%, and the growth of technology 1.6\%.

To estimate the stochastic process for the state, we first specify a vector
autoregressive AR(1) process for the event $%
s_{t}=(s_{At},s_{lt},s_{xt},s_{gt})$ of the form 
\begin{equation}
s_{t+1}=P_{0}+Ps_{t}+\varepsilon _{t+1},  \label{s process}
\end{equation}%
where the shock $\varepsilon _{t}$ is i.i.d. over time and is distributed
normally with mean zero and covariance matrix $V.$ To ensure that our
estimate of $V$ is positive semidefinite, we estimate the lower triangular
matrix $Q$, where $V=QQ^{\prime }.$ The matrix $Q$ has no structural
interpretation. (In section 5, we elaborate on the contrast between our
decomposition and more traditional decompositions which impose structural
interpretations on $Q$.)

We then use a standard maximum likelihood procedure to estimate the
parameters $P_{0},P$, and $V$ of the vector AR(1) process for the wedges. In
doing so, we use the log-linear decision rules of the prototype economy and
data on output, labor, investment, and the sum of government consumption and
net exports.

For our Great Depression experiments, we proceed as follows. We discretize
the process ($\ref{s process})$ and simulate the economy using nonlinear
decision rules from a finite-element method. We use nonlinear decision rules
in these experiments because the shocks are so large that, for a given
stochastic process, the linear decision rules are a poor approximation to
the nonlinear decision rules. Of course, we would rather have used the
nonlinear decision rules in estimating the parameters of the vector AR(1)
process. We do not do so because this exercise is computationally demanding.
Instead we experiment by varying the parameters of the vector AR(1) process
and find that our results are very similar across these experiments.

For our postwar experiments, we use the log-linear decision rules and the
continuous state process ($\ref{s process})$.

In order to implement our accounting procedure, we must first adjust the
data to make them consistent with the theory. In particular, we adjust the
U.S. data on output and its components to remove sales taxes and to add the
service flow for consumer durables. For the pre--World War II period, we
remove military compensation as well. We estimate separate sets of
parameters for the stochastic process for wedges (\ref{s process}) for each
of our two historical episodes. The other parameters are the same in the two
episodes. (See our technical appendix for our rationale for this decision.)
The stochastic process parameters for the Great Depression analysis are
estimated using annual data for 1901--40; those for analysis after World War
II, using quarterly data for 1959:1--2004:3. In the Great Depression
analysis, we impose the additional restriction that the covariance between
the shocks to the government consumption wedge and those to the other wedges
is zero. This restriction avoids having the large movements in government
consumption associated with World War I dominate the estimation of the
stochastic process.

Table I displays the resulting estimated values for the parameters of the
coefficient matrices, $P$ and $Q$, and the associated confidence bands for
our two historical data periods. The stochastic process (\ref{s process})
with these values will be used by agents in our economy to form their
expectations about future wedges.

\bigskip

\begin{center}
3.2. \emph{Findings}
\end{center}

Now we describe the results of applying our procedure to two historical U.S.
business cycle episodes. In the Great Depression, the efficiency and labor
wedges play a central role for all variables considered. In the 1982
recession, the efficiency wedge plays a central role for output and
investment while the labor wedge plays a central role for labor. The
government consumption wedge plays no role in either period. Most
strikingly, neither does the investment wedge.

In reporting our findings, we remove a trend of 1.6\% from output,
investment, and the government consumption wedge. Both output and labor are
normalized to equal 100 in the base periods: 1929 for the Great Depression
and 1979:1 for the 1982 recession. In both of these historical episodes,
investment (detrended) is divided by the base period level of output. Since
the government consumption component accounts for virtually none of the
fluctuations in output, labor, and investment, we discuss the government
consumption wedge and its components only in our technical appendix. Here we
focus primarily on the fluctuations due to the efficiency, labor, and
investment wedges.

\bigskip

\noindent a.\emph{\ }\textit{The Great Depression}

Our findings for the period 1929--39, which includes the Great Depression,
are displayed in Figures 1--4. In sum, we find that the efficiency and labor
wedges account for essentially all of the movements of output, labor, and
investment in the Depression period and that the investment wedge actually
drives output the wrong way.

In Figure 1, we display actual U.S. output along with the three measured
wedges for that period: the efficiency wedge $A,$ the labor wedge $(1-\tau
_{l}),$ and the investment wedge $1/(1+\tau _{x})$. We see that the
underlying distortions revealed by the three wedges have different patterns.
The distortions that manifest themselves as efficiency and labor wedges
become substantially worse between 1929 and 1933. By 1939, the efficiency
wedge has returned to the 1929 trend level, but the labor wedge has not.
Over the period, the investment wedge fluctuates, but investment decisions
are generally less distorted, in the sense that $\tau _{x}$ is smaller
between 1932 and 1939 than it is in 1929. Note that this investment wedge
pattern does not square with models of business cycles in which financial
frictions increase in downturns and decrease in recoveries.

In Figure 2, we plot the 1929--39 data for U.S. output, labor, and
investment along with the model's predictions for those variables when the
model includes just one wedge. In terms of the data, note that labor
declines $27\%$ from 1929 to 1933 and stays relatively low for the rest of
the decade. Investment also declines sharply from 1929 to 1933 but partially
recovers by the end of the decade. Interestingly, in an algebraic sense,
about half of output's $36\%$ fall from 1929 to 1933 is due to the decline
in investment.

In terms of the model, we start by assessing the separate contributions of
the three wedges.

Consider first the contribution of the efficiency wedge. In Figure 2, we see
that with this wedge alone, the model predicts that output declines less
than it actually does in the data and that it recovers more rapidly. For
example, by 1933, predicted output falls about $30\%$ while U.S. output
falls about $36\%$. Thus, the efficiency wedge accounts for over $80\%$ of
the decline of output in the data. By 1939, predicted output is only about $%
6\%$ below trend rather than the observed $22\%.$ As can also be seen in
Figure 2, the reason for this predicted rapid recovery is that the
efficiency wedge accounts for only a small part of the observed movements in
labor in the data. By 1933 the fall in predicted investment is similar but
somewhat greater than that in the data. It recovers faster, however.

Consider next the contributions of the labor wedge. In Figure 2, we see that
with this wedge alone, the model predicts output due to the labor wedge to
fall by 1933 a little less than half as much as output falls in the data: $%
16\%$ vs. $36\%.$ By 1939, however, the labor wedge model's predicted output
completely captures the slow recovery: it predicts output falling $21\%$,
approximately as much as output does that year in the data. This model
captures the slow output recovery because predicted labor due to the labor
wedge also captures the sluggishness in labor after 1933 remarkably well.
The associated prediction for investment is a decline, but not the actual
sharp decline from 1929 to 1933.

Summarizing Figure 2, we can say that the efficiency wedge accounts for over
three-quarters of output's downturn during the Great Depression but misses
its slow recovery, while the labor wedge accounts for about one-half of this
downturn and essentially all of the slow recovery.

Now consider the investment wedge. In Figure 3, we again plot the data for
output, labor, and investment, but this time along with the contributions to
those variables that the model predicts are due to the investment wedge
alone. This figure demonstrates that the investment wedge's contributions
completely miss the observed movements in all three variables. The
investment wedge actually leads output to rise by about $9\%$ by 1933.

Together, then, Figures 2 and 3 suggest that the efficiency and labor wedges
account for essentially all of the movements of output, labor, and
investment in the Depression period and that the investment wedge accounts
for almost none. This suggestion is confirmed by Figure 4. There we plot the
combined contribution from the efficiency, labor, and (insignificant)
government consumption wedges (labeled \emph{Model With No Investment Wedge}%
). As can be seen from the figure, essentially all of the fluctuations in
output, labor, and investment can be accounted for by movements in the
efficiency and labor wedges. For comparison, we also plot the combined
contribution due to the labor, investment, and government consumption wedges
(labeled \emph{Model With No Efficiency Wedge}). This combination does not
do well. In fact, comparing Figures 2 and 4, we see that the model with this
combination is further from the data than the model with the labor wedge
component alone.

One issue of possible concern with our findings about the role of the
investment wedge is that measuring it is subtler than measuring the other
wedges. Recall that the measurement of this wedge depends on the details of
the stochastic process governing the wedges, whereas the size of the other
wedges can be inferred from static equilibrium conditions. To address this
concern, we conduct an additional experiment intended to give the model with
no efficiency wedge the best chance of accounting for the data.

In this experiment, we choose the investment wedge to be as large as it
needs to be for investment in the model to be as close as possible to
investment in the data, and we set the other wedges to be constants.
Predictions of this model, which we call the \emph{Model With Maximum
Investment Wedge}, turn out to poorly match the behavior of consumption in
the data. For example, from 1929 to 1933, consumption in the model rises
more than $8\%$ relative to trend while consumption in the data declines
about $28\%.$ (For details, see the technical appendix.) We label this poor
performance the \textit{consumption anomaly} of the investment wedge model.

Altogether, these findings lead us to conclude that distortions which
manifest themselves primarily as investment wedges played essentially no
useful role in the U.S. Great Depression.\bigskip

\noindent b.\emph{\ The 1982 Recession}

Now we apply our accounting procedure to a more typical U.S. business cycle:
the recession of 1982. Here we get basically the same results as with the
earlier period: the efficiency and labor wedges play primary roles in the
business cycle fluctuations, and the investment wedge plays essentially none.

We start here as we did in the Great Depression analysis, by displaying
actual U.S. output over the entire business cycle period---here,
1979--85---along with the three measured wedges for that period. In Figure
5, we see that output falls nearly $10\%$ relative to trend between 1979 and
1982 and by 1985 is back up to about $1\%$ below trend. We also see that the
efficiency wedge falls between 1979 and 1982 and by 1985 is still a little
more than $3\%$ below trend. The labor wedge also worsens from 1979 to 1982,
but it improves substantially by 1985. The investment wedge, meanwhile,
fluctuates until 1983 and improves thereafter.

An analysis of the effects of the wedges separately for the 1979--85 period
is in Figures 6 and 7. In Figure 6, we see that the model with the
efficiency wedge alone produces a decline in output from 1979 to 1982 of $%
6\% $, which is about $60\%$ of the actual decline in that period. Here
output recovers a bit more slowly than in the data, but seems to otherwise
generally parallel the data's movements. The model with the labor wedge
alone produces a decline in output from 1979 to 1982 of only about $3\%.$ In
Figure 7, we see that the model with just the investment wedge produces
essentially no fluctuations in output.

Now we examine how well a combination of wedges reproduces the data for the
1982 recession period just as we did for the Depression period. In Figure 8,
we plot the movements in output, labor, and investment during 1979--85 due
to two combinations of wedges. One is the combined effects of the
efficiency, labor, and (insignificant) government consumption components
(labeled \emph{Model With No Investment Wedge}). In terms of output, this
combination mimics the decline in output until 1982 extremely well and
produces a slightly shallower recovery than in the data. The other is the
combination of the labor, investment, and government components (labeled 
\emph{Model With No Efficiency Wedge}), which produces a modest decline in
output relative to the data. In Figures 6, 7, and 8, we see clearly that in
the model with no efficiency wedge the labor wedge accounts for essentially
all of the decline and the investment wedge, essentially none. \bigskip

\begin{center}
3.3. \emph{Extending the Analysis to the Entire Postwar Period}
\end{center}

So far we have analyzed the wedges and their contributions for specific
episodes. The findings for both episodes suggest that frictions in detailed
models which manifest themselves as investment wedges in the benchmark
prototype economy play, at best, a tertiary role in accounting for business
cycle fluctuations. Do our findings apply beyond those particular episodes?
We attempt to extend our analysis to the entire postwar period by developing
some summary statistics for the period from 1959:1 through 2004:3 using
HP-filtered data. We first consider the standard deviations of the wedges
relative to output as well as correlations of the wedges with each other and
with output at various leads and lags. We then consider the standard
deviations and the cross correlations of output due to each wedge. These
statistics summarize salient features of the wedges and their role in output
fluctuations for the entire postwar sample. We think of the wedge statistics
as analogs of our plots of the wedges and the output statistics as analogs
of our plots of output due to just one wedge.\footnote{%
In Chari, Kehoe, and McGrattan (2004), we apply a spectral method to
determine the contributions of the wedges based on the population properties
of the stochastic process generated by the model. We do this for both
periods and find that the investment wedge plays only a modest role in both.}
The results suggest that our earlier findings do hold up, at least in a
relative sense: the investment wedge seems to play a larger role over the
entire postwar period than in the 1982 recession, but its effects are still
quite modest compared to those of the other wedges.

In Tables II and III, we display standard deviations and cross correlations
calculated using HP-filtered data for the postwar period. Panel A of Table
II shows that the efficiency, labor, and investment wedges are positively
correlated with output both contemporaneously and for several leads and
lags. In contrast, the government consumption wedge is somewhat negatively
correlated with output, both contemporaneously and for several leads and
lags. (Note that the government consumption wedge is the sum of government
consumption and net exports and that net exports are negatively correlated
with output.) Panel B of Table II shows that the cross correlations of the
efficiency, labor, and investment wedges are generally positive.

Table III summarizes various statistics of the movements of output over this
period due to each wedge. Consider panel A, and focus first on the output
fluctuations due to the efficiency wedge. Table III shows that output
movements due to this wedge have a standard deviation which is $73\%$ of
that of output in the data. These movements are highly positively correlated
with output in the data, both contemporaneously and for several leads and
lags. These statistics are consistent with our episodic analysis of the $%
1982 $ recession, which showed that the efficiency wedge can account for
about 60\% of the actual decline in output during that period and comoves
highly with it.

Consider next the role of the other wedges in the entire postwar period.
Return to Table III. In panel A, again, we see that output due to the labor
wedge alone fluctuates almost $60\%$ as much as does output in the data and
is positively correlated with it. Output due to the investment wedge alone
fluctuates less than a third as much as output in the data and is somewhat
positively correlated with it. Finally, output due to the government
consumption wedge alone fluctuates about $40\%$ as much as output in the
data and is somewhat negatively correlated with it. In panel B of Table III,
we see that output movements due to the efficiency and labor wedges as well
as the efficiency and investment wedges are positively correlated and that
the cross correlations of output movements due to the other wedges are
mostly essentially zero or negative.

All of our analyses using business cycle accounting thus seem to lead to the
same conclusion: to study business cycles, the most promising detailed
models to explore are those in which frictions manifest themselves primarily
as efficiency or labor wedges, not as investment wedges.

\bigskip

\begin{center}
4. \textsc{Interpreting Wedges With }\\[0pt]
\textsc{Alternative Technology or Preference Specifications}
\end{center}

In detailed economies with technology and preferences similar to those in
our benchmark prototype economy, the equivalence propositions proved thus
far provide a mapping between frictions in those detailed economies and
wedges in the prototype economy. Here we construct a similar mapping when
technology or preferences differ in the two types of economies. We then ask
if this alternative mapping changes our substantive conclusion that
financial frictions which manifest themselves primarily as investment wedges
are unlikely to play a primary role in accounting for business cycles. We
find that it does not.

When detailed economies have technology or preferences different from the
benchmark economy's, wedges in the benchmark economy can be viewed as
arising from two sources: frictions in the detailed economy and differences
in the specification of technology or preferences. While researchers could
simply use results from our benchmark prototype economy to draw inferences
about promising classes of models, drawing such inferences is easier with an
alternative approach. Basically, we decompose the wedges into their two
sources. To do that, construct an alternative prototype economy with
technology and preferences that do coincide with those in the detailed
economy, and repeat the business cycle accounting procedure with those two
economies. The part of the wedges in the benchmark prototype economy due to
frictions, then, will be the wedges in the alternative prototype economy,
while the remainder will be due to specification differences.

Here we use this approach to explore alternative prototype economies with
technology and preference specifications chosen because of their popularity
in the literature. These alternative specifications include variable instead
of fixed capital utilization, different labor supply elasticities, and
varying levels of costs to adjusting investment.

Two of these changes offer no help to investment wedges. Adding variable
capital utilization to the analysis shifts the relative contributions of the
efficiency and labor wedges to output's fluctuations---decreasing the
efficiency wedge's contribution and increasing the labor wedge's---but this
alternative specification leaves the investment wedge's contribution
definitely in third place. Adding different labor elasticities to the
analysis offers no help either.

The third specification change seems to give investment wedges a slightly
larger role, but still not a primary one. With investment adjustment costs
added to the analysis, the investment wedge in the benchmark prototype
economy depends on both the investment wedge and the marginal cost of
investment in the alternative prototype economy. We find that even if the
investment wedge is constant in the benchmark economy, it will worsen during
recessions and improve during booms in the alternative economy. With our
measured wedges, this finding suggests that with large enough adjustment
costs, investment wedges in detailed economies could play a significant role
in business cycle fluctuations.

To study this possibility, we investigate the effects of two parameter
values for adjustment costs: one at the level used by Bernanke, Gertler, and
Gilchrist (1999), the \emph{BGG level}, and one we consider \emph{extreme},
at four times that level. For the Great Depression period, we find that for
both adjustment cost levels, investment wedges play only a minor role. For
the 1982 recession period, we find that these wedges play a very small role
with BGG level costs and a somewhat larger but still modest role with the
much higher costs. These findings suggest that researchers who think
adjustment costs are extremely high may want to include in their models
financial frictions that manifest themselves as investment wedges. Such
models are not likely to do well, however, unless they also include other
frictions that play the primary role in business cycle fluctuations.

\bigskip

\begin{center}
4.1. \emph{Details of Alternative Specifications}
\end{center}

\noindent a. \emph{Variable Capital Utilization}

We begin with an extreme view about the amount of variability in capital
utilization.

Our specification of the technology which allows for variable capital
utilization follows the work of Kydland and Prescott (1988) and Hornstein
and Prescott (1993). We assume that the production function is now 
\begin{equation}
y=A(kh)^{\alpha }(nh)^{1-\alpha },  \label{variable y}
\end{equation}%
where $n$ is the number of workers employed and $h$ is the length (or \emph{%
hours}) of the workweek. The labor input is, then, $l=nh.$

In the data, we measure only the labor input $l$ and the capital stock $k$.
We do not directly measure $h$ or $n.$ The benchmark specification for the
production function can be interpreted as assuming that all of the observed
variation in measured labor input $l$ is in the number of workers and that
the workweek $h$ is constant$.$ Under this interpretation, our benchmark
specification with \emph{fixed capital utilization} correctly measures the
efficiency wedge (up to the constant $h).$

Now we investigate the opposite extreme: assume that the number of workers $%
n $ is constant and that all the variation in labor is from the workweek $h.$
Under this\textit{\ variable capital utilization} specification, the
services of capital $kh$ are proportional to the product of the stock $k$
and the labor input $l,$ so that variations in the labor input induce
variations in the flow of capital services. Thus, the capital utilization
rate is proportional to the labor input $l,$ and the efficiency wedge is
proportional to $y/k^{\alpha }.$

Consider an alternative prototype economy, denoted \emph{economy 2},
identical to a deterministic version of our benchmark prototype economy,
denoted \emph{economy 1}, except that the production function is now given
by $y=Ak^{\alpha }l.$ Let the sequence of wedges and the equilibrium
outcomes in the two economies be $(A_{it},\tau _{lit},\tau _{xit})$ and $%
(y_{it},c_{it},l_{it},x_{it})$ for $i=1,2.$ We then have this proposition:

\bigskip

\textsc{Proposition }3:\textit{\ }\emph{If the sequence of wedges for an
alternative prototype economy }2\emph{\ are related to the wedges in the
prototype economy }1\emph{\ by }$A_{2t}=A_{1t}l_{1t}^{-\alpha }$, $1-\tau
_{l2t}=$ $(1-\alpha )(1-\tau _{l1t}),$ \emph{and} $\tau _{x2t}=\tau _{x1t},$ 
\emph{then the equilibrium outcomes for the two economies coincide. }
\bigskip

\textsc{Proof:} We prove this proposition by showing that the equilibrium
conditions of economy $2$ are satisfied at the equilibrium outcomes of
economy $1.$ Since $y_{1t}=A_{1t}k_{1t}^{\alpha }l_{1t}^{1-\alpha },$ using
the definition of $A_{2t},$ we have that $y_{1t}=A_{2t}k_{1t}^{\alpha
}l_{1t}.$ The first-order condition for labor in economy $1$ is 
\[
-\frac{U_{lt}(c_{1t},l_{1t})}{U_{ct}(c_{1t},l_{1t})}=(1-\tau _{l1t})\frac{%
(1-\alpha )y_{1t}}{l_{1t}}. 
\]%
Using the definition of $\tau _{l2t},$ we have that 
\[
-\frac{U_{lt}(c_{1t},l_{1t})}{U_{ct}(c_{1t},l_{1t})}=(1-\tau _{l2t})\frac{%
y_{1t}}{l_{1t}}. 
\]%
The rest of the equations governing the equilibrium are unaffected. 
%TCIMACRO{\TeXButton{TeX field}{\hspace{1.75in}} }%
%BeginExpansion
\hspace{1.75in}
%EndExpansion
$\ \ Q.E.D.$

\bigskip

Note that even if the efficiency wedge in the alternative prototype economy
does not fluctuate, the associated efficiency wedge in the prototype economy
will. Proposition 3 also implies that if $\tau _{x1t}$ is a constant, so
that the contribution of the investment wedge to fluctuations in economy $1$
is zero, then $\tau _{x2t}$ is also a constant; hence, the contribution of
the investment wedge to fluctuations in economy $2$ is also zero. Extending
this proposition to a stochastic environment is immediate.

Now suppose that we are interested in detailed economies with variable
capital utilization. We use the alternative prototype economy to ask whether
this change affects our substantive conclusions. In answering this question,
we reestimate the parameters of the stochastic process for the underlying
state. (For details, see the technical appendix.)\ 

Variable capital utilization can induce significant changes in the measured
efficiency wedge. To see these changes, in Figure 9, we plot the measured
efficiency wedges for these two specifications of capital utilization during
the Great Depression period (with it \emph{fixed} in the benchmark economy
and \emph{variable} now). Clearly, when capital utilization is variable
rather than fixed, the efficiency wedge falls less and recovers more by
1939. (For the other wedges, see the technical appendix).

In Figure 10, we plot the data and the predicted output due to the
efficiency and labor wedges for the 1930s when the model includes variable
capital utilization. Comparing Figures 10 and 2, we see that with the
remeasured efficiency wedge, the labor wedge plays a much larger role in
accounting for the output downturn and slow recovery and\ the efficiency
wedge plays a much smaller role.

In Figure 11, we plot the three data series again, this time with the
predictions of the variable capital utilization model with just the
investment wedge. Comparing this to Figure 3, we see that with variable
capital utilization, the investment wedge drives output the wrong way to an
even greater extent than in the benchmark economy.

In Figure 12, we compare the contributions of the sum of the efficiency and
labor wedges for the two specifications of capital utilization (fixed and
variable) during the Great Depression period. The figure shows that these
contributions are quite similar. While remeasuring the efficiency wedge
changes the relative contributions of the two wedges, it clearly has little
effect on their combined contribution.

Overall, then, taking account of variable capital utilization strengthens
our finding that in the Great Depression period, the efficiency and labor
wedges play a primary role and investment wedges do not.

\bigskip

\noindent b. \emph{Different Labor Supply Elasticities}

Now we consider the effects on our results of changing the elasticity of
labor supply. We assume in our benchmark model that preferences are
logarithmic in both consumption and leisure. Consider now an alternative
prototype economy with a different elasticity of labor supply. We show that
a result analogous to that in Proposition 3 holds: allowing for different
labor supply elasticities changes the size of the measured labor wedge but
not that of the measured investment wedge. Therefore, if the contribution of
the investment wedge is zero in the benchmark prototype economy, it is also
zero in an economy with a different labor supply elasticity.

To see that, consider an alternative prototype economy which is identical to
a deterministic version of our benchmark model except that now the utility
function is given by $U(c)+V_{2}(1-l)$. Denote the utility function in our
benchmark prototype economy (economy 1) by $U(c)+V_{1}(1-l).$ Clearly, by
varying the function $V_{2},$ we can generate a wide range of alternative
labor supply elasticities.

Let the sequence of wedges and the equilibrium outcomes in the two economies
be $(A_{it},\tau _{lit},\tau _{xit})$ and $(y_{it},c_{it},l_{it},x_{it})$
for $i=1,2.$ We then have this proposition:

\bigskip

\textsc{Proposition }4: \emph{If the sequence of wedges for the alternative
prototype economy, economy }2,\emph{\ is given by } 
\[
1-\tau _{l2t}=(1-\tau _{l1t})\frac{V_{2}^{\prime }(1-l_{1t})}{V_{1}^{\prime
}(1-l_{1t})}, 
\]%
\emph{and if} $A_{2t}=A_{1t}$ \emph{and} $\tau _{x2t}=\tau _{x1t},$ \emph{%
then the equilibrium outcomes for the two economies coincide. }\bigskip

\textsc{Proof:} We prove this proposition by showing that the equilibrium
conditions of economy $2$ are satisfied at the equilibrium outcomes of
economy $1.$ The first-order condition for labor input in economy $1$ is 
\[
-\frac{V_{1}^{\prime }(1-l_{1t})}{U^{\prime }(c_{1t})}=(1-\tau _{l1t})\frac{%
(1-\alpha )y_{1t}}{l_{1t}}. 
\]%
Using the definition of $\tau _{l2t},$ we have that 
\[
-\frac{V_{2}^{\prime }(1-l_{1t})}{U^{\prime }(c_{1t})}=(1-\tau _{l2t})\frac{%
(1-\alpha )y_{1t}}{l_{1t}}, 
\]%
so that the first-order condition for labor in economy 2 is satisfied. The
rest of the equations governing the equilibrium are unaffected. 
%TCIMACRO{\TeXButton{TeX field}{\hspace{4.5in}} }%
%BeginExpansion
\hspace{4.5in}
%EndExpansion
$Q.E.D.$

\bigskip

Note that here even if the labor wedge does not fluctuate in our benchmark
prototype economy, it typically will in the alternative prototype economy.
Note also that the investment wedges are the same in both economies. Thus,
if the investment wedge is constant in one economy, it is constant in the
other; and the contribution of the investment wedge to fluctuations is zero
in both economies. Extending this proposition to a stochastic environment is
immediate.

\bigskip

\noindent c. \emph{Investment Adjustment Costs}

Now we consider a third alternative prototype economy, this one with
investment adjustment costs. These costs can be interpreted as standing in
for one of two features of detailed economies. One is that the detailed
economies have adjustment costs in converting output into installed capital.
Another interpretation is that the detailed model does not have adjustment
costs, but that financial frictions manifest themselves as adjustment costs
in the alternative prototype economy (as in Bernanke and Gertler (1989) and
Carlstrom and Fuerst (1997)).

In this alternative prototype economy, the only difference from the
benchmark prototype economy is that the capital accumulation law is no
longer (\ref{1}), but rather is%
\begin{equation}
(1+\gamma _{n})k_{t+1}=(1-\delta )k_{t}+x_{t}-\phi \left( \frac{x_{t}}{k_{t}}%
\right) k_{t},  \label{capital adjust}
\end{equation}%
where $\phi $ represents the per unit cost of adjusting the capital stock.
In the macroeconomic literature, a commonly used functional form for the
adjustment costs $\phi $ is 
\begin{equation}
\phi \left( \frac{x}{k}\right) =\frac{a}{2}\left( \frac{x}{k}-b\right) ^{2},
\label{adjustment}
\end{equation}%
where $b=\delta +\gamma +\gamma _{n}$ is the steady-state value of the
investment-capital ratio.

To set up the analog of Propositions 3 and 4, let the wedges in the
benchmark prototype economy, economy 1, and the alternative prototype
economy, economy 2, be $(A_{it},\tau _{lit},\tau _{xit})$ and $%
(y_{it},c_{it},l_{it},x_{it})$ for $i=1,2.$ For simplicity, let $\tau _{x2t}$
and $g_{2t}$ be identically zero. The proof of the following proposition is
immediate.

\bigskip

\textsc{Proposition }5: \emph{If the sequence of wedges for the alternative
prototype economy, economy }2,\emph{\ is given by }$A_{2t}=A_{1t},\tau
_{l2t}=\tau _{l1t},$ $\tau _{x1t}$ implicitly defined by\emph{\ } 
\begin{equation}
\frac{A_{1t+1}F_{kt+1}+(1-\delta )(1+\tau _{x1t+1})}{1+\tau _{x1t}}=\frac{%
A_{2t+1}F_{kt+1}+(1-\delta +\phi _{t}-x_{2t+1}\phi _{t+1}^{\prime
}/k_{2t+1})(1-\phi _{t+1}^{\prime })^{-1}}{(1-\phi _{t}^{\prime })^{-1}},
\label{phi}
\end{equation}%
\emph{and }$g_{1t}=\phi _{t}k_{2t},$ \emph{then the equilibrium outcomes for
the two economies coincide}$.$ \bigskip

In understanding the investment wedge $\tau _{x1t}$, note that if adjustment
costs are given by (\ref{adjustment}), then the term $\phi _{t}-x_{t+1}\phi
_{t+1}^{\prime }/k_{t+1}$ in (\ref{phi}) equals $a[(x/k)^{2}-b^{2}]/2$,
which is an order of magnitude smaller than $\phi _{t}^{\prime }=a[x/k-b].$
Setting this term to zero gives the approximation 
\begin{equation}
1+\tau _{x1t}=\frac{1}{1-\phi _{t}^{\prime }}.  \label{approx}
\end{equation}%
>From (\ref{approx}) and the convexity of $\phi $, we see that $\tau _{x1}$
is increasing in $x/k$ and is zero when $x/k$ is at its steady-state value.
Hence, in recessions, when $x/k$ is relatively low, $\tau _{x1}$ is
negative; and in booms, when $x/k$ is relatively high, $\tau _{x1}$ is
positive. In this sense, even when the alternative prototype economy has no
investment wedges, $\tau _{x1}$ will be countercyclical in the benchmark
prototype economy, so investment distortions will be smaller in recessions.

Note, more generally, that when investment wedges in the alternative
prototype economy are nonzero, the analog of (\ref{approx}) is 
\begin{equation}
1+\tau _{x1t}=\frac{1+\tau _{x2t}}{1-\phi _{t}^{\prime }}.  \label{approx2}
\end{equation}

We can also use the equivalence map in (\ref{approx2}) in the reverse
direction. Imagine that the data are generated from a detailed economy with
no adjustment costs and no frictions. The benchmark prototype economy will
have $\tau _{x1t}=0.$ Suppose a researcher considers an alternative
prototype economy with adjustment costs. This researcher will find that $%
1+\tau _{x2t}=1-\phi _{t}^{\prime }$, so that the investment wedge will be
procyclical even though the detailed economy has no frictions.

More generally, a researcher who incorrectly specifies too high a level of
adjustment costs in the alternative prototype economy will infer that
investment wedges play a much larger role than they actually do. To get some
intuition for this result, consider two alternative prototype economies $A$
and $B$, both of which have investment wedges and adjustment costs. The
analog of our approximation (\ref{approx2}) is $(1+\tau _{xAt})/(1-\phi
_{At}^{\prime })=(1+\tau _{xBt})/(1-\phi _{Bt}^{\prime })$, where $\phi
_{it} $ denotes adjustment costs in economy $i=A,B.$ Straightforward algebra
establishes that specifying too high a level of adjustment costs makes
investment wedges seem worse in recessions than they actually are.

Now we consider a prototype economy with adjustment costs and ask whether
our substantive conclusion that the investment wedge plays at most a
tertiary role in either the Great Depression or postwar business cycles is
affected. We follow Bernanke, Gertler, and Gilchrist (1999) in how we choose
the value for the parameter $a.$ Bernanke, Gertler, and Gilchrist (BGG)
choose this parameter so that the elasticity, $\eta ,$ of the price of
capital with respect to the investment-capital ratio is $.25.$ In this
setup, the price of capital $q=1/(1-\phi ^{\prime }),$ so that, evaluated at
the steady state, $\eta =a(\delta +\gamma +\gamma _{n}).$ Given our other
parameters, $a=3.22.$ In Figures 13 and 14, this parameterization is labeled
as the model with \emph{BGG Costs. }Bernanke, Gertler, and Gilchrist also
argue that a reasonable range for the elasticity $\eta $ is between $0$ and $%
.5$, that values much outside this range imply implausibly high adjustment
costs. We consider an extreme case in which $\eta =1$, so that $a=12.88$,
roughly four times the BGG level. In the figures, this parameterization is
labeled as the model with \emph{Extreme Costs. }For each setting of the
parameter $a$, we reestimate the stochastic process for the state. (For the
parameter values of the stochastic process, see the technical appendix.)

Comparing the investment wedges in Figure 1 and panel A of Figure 13, we see
that introducing investment adjustment costs leads the investment wedge to
worsen rather than improve in the early part of the Great Depression. In
panel A of Figure 14 we see that this worsening produces a decline in output
from 1929 to 1933. With the BGG adjustment costs, however, the decline is
tiny $(2\%$ from 1929 to 1933). Even with the extreme adjustment costs, the
decline is only $6.5\%$ and, hence, accounts for only about one-sixth of the
overall decline in output.\footnote{%
In general, in our Great Depression experiments, linear methods perform
poorly compared to our nonlinear method. With extreme adjustment costs, for
example, linear methods produce large errors, on the order of $100\%$.}
Moreover, with these extreme adjustment costs, the consumption anomaly
associated with investment wedges is acute. For example, from 1929 to 1932,
relative to trend, consumption in the data falls about $18\%$, while in the
model it actually rises by more than $5\%.$

We are skeptical that detailed models with extreme adjustment costs are
worth exploring. With extreme costs, given the observed levels of investment
and the capital stock in the data, (\ref{adjustment}) implies that the
resources lost due to adjustment costs as a fraction of output are nearly $%
7\%$ in 1933. We share Bernanke, Gertler, and Gilchrist's (1999) concerns
that costs of this magnitude are implausibly large. From 1929 to 1933,
investment falls sharply, but the adjustment costs implied by (\ref%
{adjustment}) rise sharply. Why would firms incur adjustment costs simply by
investing at positive rates below their steady-state value? The idea that
managers incurred huge adjustment costs simply because they were watching
their machines depreciate seems farfetched. Furthermore, the idea that from
1929 to 1933 investment fell sharply but adjustment costs rose sharply is
inconsistent with interpreting these costs as arising from monitoring costs
in an economy with financial frictions. Indeed, in such an economy, as
investment activity falls, so do monitoring costs.

We do similar experiments for the 1982 recession period, with similar
results. In panel B of Figure 13, we see that with BGG costs the investment
wedge fluctuates little through the end of 1982 and improves thereafter.
With extreme costs the investment wedges worsens until 1983 and improves
thereafter. Panel B of Figure 14 shows that in the model with costs at the
BGG level, the investment wedge plays essentially no role in output
fluctuations. With costs at four times the BGG level, the panel shows that
the investment wedge plays a bit larger but still modest role. Recall that,
relative to trend, output in the data falls almost 10\% from its peak to its
trough. With extreme adjustment costs, output due to the investment wedge
falls about 2.2\%, so that the investment wedge appears to account for
roughly one-fifth of the fall in output.

In our judgment, the investment wedge actually accounts for much less than
one-fifth of the 1982 recession fall in output because we think extreme
adjustment costs are implausible. Even aside from the Great Depression
issues, we find models with extreme adjustment costs difficult to reconcile
with data on plant level investment decisions. An extensive literature has
documented that investment at the plant level has large spikes. Doms and
Dunne (1994), for example, examine plant level data for 33,000 plants over
17 years. They show that much of the growth in the capital stock of a plant
is concentrated in a short period of time. In the year of highest
investment, the capital stock grows 45\%, while in the years immediately
before and after that, it grows less than 10\%. Such behavior is clearly
inconsistent with extreme adjustment costs.

Furthermore, the use of adjustment costs in macroeconomic analysis is
controversial. Kydland and Prescott (1982), for example, have argued that
models with adjustment costs like those in equation (\ref{adjustment}) are
inconsistent with the data. Such models imply a static relationship between
the investment-capital ratio and the relative price of investment goods to
output (of the form $q=1/[1-\phi ^{\prime }(x/k)]$). This means that the
elasticity of the investment-capital ratio with respect to the relative
price is the same in the short run and the long run. Kydland and Prescott
argue that this is not consistent with the data, where short-run
elasticities are much smaller than long-run elasticities.

Finally, the finding that investment wedges play a modest role when
adjustment costs are extreme is easy to reconcile with the view that
financial frictions which manifest themselves primarily as investment wedges
play a small role over the business cycle. This reconciliation uses the
insight discussed above that a modeler who incorrectly specifies too high a
level of adjustment costs will incorrectly find too large a role for
investment wedges.

\bigskip

\begin{center}
5. \textsc{Contrasting Our Decomposition With Traditional Decompositions}
\end{center}

Our decomposition of business cycle fluctuations is intended to isolate the
partial effects of each of the wedges on equilibrium outcomes, and in this
sense, it is different from traditional decompositions. Those decompositions
attempt to isolate the effects of (so-called) primitive shocks on
equilibrium outcomes; ours does not. Isolating the effects of primitive
shocks requires specifying a detailed model. Since our procedure precedes
the specification of a detailed model, it obviously cannot be used to
isolate the effects of primitive shocks. In order to clarify the distinction
between our decomposition and a traditional one, here we describe a
traditional decomposition and explain why we prefer ours.

The traditional decomposition attempts to isolate the effects of primitive
shocks by \textquotedblleft naming the innovations.\textquotedblright\
Recall that in our stochastic process for the four wedges, (\ref{s process}%
), the innovations $\varepsilon _{t+1}$ are allowed to be contemporaneously
correlated with the covariance matrix $V.$ Under the traditional
decomposition, the primitive shocks, say, $\eta _{t+1}$, are assumed to be
mean zero, to be contemporaneously uncorrelated with $E\eta _{t+1}\eta
_{t+1}^{\prime }=I$, and to lead to the same stochastic process for the
wedges. Identifying these primitive shocks requires specifying a matrix $R$
so that $R\eta _{t+1}=\varepsilon _{t+1}$ and $RR^{\prime }=V.$ Names are
then made up for these shocks, including \emph{money} shocks, \emph{demand}
shocks, \emph{technology} shocks, and so on.

In the traditional method, then, given any sequence of realized wedges $%
s_{t} $ and the specification of the matrix $R$, the associated realized
values of $\eta _{t}=(\eta _{1t},\eta _{2t},\eta _{3t},\eta _{4t})^{\prime }$
are computed. The movements in, say, output, are then decomposed into the
movements due to each one of these primitive shocks as follows. Let $%
s_{t}(\eta _{1})=$ {\large (}$\log A_{t}(\eta _{1}),\tau _{lt}(\eta _{1})$, $%
\tau _{xt}(\eta _{1}),\log g_{t}(\eta _{1})${\large )} denote the realized
values of the four wedges when the primitive shock sequence $\eta _{t}=(\eta
_{1t},0,0,0)$ is fed into 
\[
s_{t+1}=P_{0}+Ps_{t}+R\eta _{t+1}. 
\]%
(Note that when the covariance matrix $V$ is not diagonal, movements in a
primitive shock $\eta _{1t}$ will lead to movements in more than one wedge.)
The predicted value of, say, output due to $\eta _{1}$ is then computed from
the decision rules of the model according to $y_{t}(\eta _{1})=y${\large (}$%
k_{t}(\eta _{1}),s_{t}(\eta _{1})${\large )}, where $k_{t}(\eta _{1})$ is
computed recursively using the decision rule for investment, the initial
capital stock, and the capital accumulation law. The values $s_{t}(\eta
_{2}) $, $y_{t}(\eta _{2})$, and the rest are computed in a similar way.

Notice that in this traditional decomposition method, the realized value of
each wedge is simply the sum of the parts due to $\eta _{1},\eta _{2},$ and
so on, in that 
\[
\log A_{t}=\sum_{i}\log A_{t}(\eta _{i}),~\tau _{lt}=\sum_{i}\tau _{lt}(\eta
_{i}),~\tau _{xt}=\sum_{i}\tau _{xt}(\eta _{i}),~\log g_{t}=\sum_{i}\log
g_{t}(\eta _{i}). 
\]%
In this sense, the traditional decomposition attempts to decompose each of
the four wedges into four component parts, each of which is due to a
primitive shock.

Our decomposition is purposefully less ambitious. It includes only the
effect of the movements of each total wedge, not any of its subparts. The
advantage of our decomposition is that it is invariant to $R$, so that we do
not need to make identifying assumptions implicit in the specification of
the matrix $R,$ nor do we need to make up names for the shocks. The
invariance makes our method valuable. The problem with the traditional
approach is that finding identifying assumptions that apply to a broad class
of detailed models is very difficult. Hence, this approach is not useful in
pointing researchers toward classes of promising models. In a sense, the
traditional approach puts the cart before the horse: the decomposition
requires specifying the matrix $R$, but doing that requires a detailed
model. Our decomposition is useful precisely because it does not need to
make up identifying assumptions to specify the matrix $R.$ Our equivalence
results have identifying assumptions built into them, so that results from
the benchmark prototype economy can be used to uncover promising classes of
detailed models.

\bigskip

\begin{center}
6. \textsc{Reviewing the Related Literature}
\end{center}

Our work here is related to the existing literature in terms of methodology
and the interpretation of the wedges.

\bigskip \newpage

\begin{center}
6.1. \emph{Methodology}
\end{center}

Our basic method is to use restrictions from economic theory to back out
wedges from the data, formulate stochastic processes for these wedges, and
then put the wedges back into a quantitative general equilibrium model for
an accounting exercise. This basic idea is at the heart of an enormous
amount of work in the real business cycle theory literature. Prescott
(1986), for example, asks what fraction of the variance of output can
plausibly be attributed to productivity shocks, which we have referred to as
the \emph{efficiency wedge}. Subsequent studies have expanded this general
equilibrium accounting exercise to include a wide variety of other shocks.
(See, for example, the studies in Cooley's 1995 volume.)

An important difference between our method and others is that we back out
the labor wedge and the investment wedge from the combined consumer and firm
first-order conditions, while most of the recent business cycle literature
uses direct measures of labor and investment shocks. Perhaps the most
closely related precursor of our method is McGrattan's (1991); she uses the
equilibrium of her model to infer the implicit wedges. Ingram, Kocherlakota,
and Savin (1997) advocate a similar approach.

\bigskip

\begin{center}
6.2. \emph{Wedge Interpretations}
\end{center}

The idea that taxes of various kinds distort the relation between various
marginal conditions is the cornerstone of public finance. Taxes are not the
only well-known distortions; monopoly power by unions or firms is also
commonly thought to produce a labor wedge. And the idea that a labor wedge
is produced by sticky wages or sticky prices is the cornerstone of the new
Keynesian approach to business cycles; see, for example, the survey by
Rotemberg and Woodford (1999). One contribution of our work here is to show
the precise mapping between the wedges and general equilibrium models with
frictions.

Many studies have plotted one or more of the four wedges. The efficiency
wedge has been extensively studied. (See, for example, Kehoe and Prescott
(2002).) The labor wedge has also been studied. For example, Parkin (1988),
Hall (1997), and Gal\'{\i}, Gertler, and L\'{o}pez-Salido (forthcoming) all
graph and interpret the labor wedge for the postwar data. Parkin discusses
how monetary shocks might drive this wedge, and Hall discusses how search
frictions might drive it. Gal\'{\i}, Gertler, and L\'{o}pez-Salido discuss a
variety of interpretations of the labor wedge, as do Rotemberg and Woodford
(1991, 1999). Mulligan (2002a, b) plots the labor wedge for the United
States for much of the 20th century, including the Great Depression period.
He interprets movements in this wedge as arising from changes in labor
market institutions and regulation, including features we discuss here. Cole
and Ohanian (2002) plot the labor wedge for the Great Depression and offer
interpretations similar to ours. The investment wedge has been investigated
by McGrattan (1991), Braun (1994), Carlstrom and Fuerst (1997), and Cooper
and Ejarque (2000).

\bigskip

\begin{center}
7. \textsc{Conclusions and Extensions}
\end{center}

This study is aimed at applied theorists who are interested in building
detailed, quantitative models of economic fluctuations. Once such theorists
have chosen the primitive sources of shocks to economic activity, they need
to choose the mechanisms through which the shocks lead to business cycle
fluctuations. We have shown that these mechanisms can be summarized by their
effects on four wedges in the standard growth model. Our business cycle
accounting method can be used to judge which mechanisms are promising and
which are not, thus helping theorists narrow their options. We view our
method as an alternative to the use of structural vector autoregressions
(VARs), which has also been advocated as a way to identify promising
mechanisms. (Elsewhere, in Chari, Kehoe, and McGrattan (2005), we argue that
structural VARs have deficiencies that limit their usefulness.)

Here we have demonstrated how our method works by applying it to two
historical episodes, the Great Depression and the 1982 U.S. recession. We
have found that efficiency and labor wedges, in combination, account for
essentially all of the decline and recovery in these business cycles;
investment wedges play, at best, a tertiary role. These results hold in
summary statistics of the entire postwar period and in alternative
specifications of the growth model. We have also found that when we maximize
the contribution of the investment wedge, the models display a consumption
anomaly: they tend to produce much smaller declines in consumption during
downturns than occur in the data. These findings together imply that
existing models of financial frictions in which the distortions primarily
manifest themselves as investment wedges can account, at best, for only a
small fraction of the fluctuations in the Great Depression or more typical
U.S. downturns. This finding is our primary substantive contribution.

We have seen that if adjustment costs are extreme, investment wedges can
play a larger but still modest role over the business cycle. A combination
of microeconomic and macroeconomic observations argue against extreme
adjustment costs, and we view them as a theoretical curiosity of no applied
interest.

A useful extension of our work here would be to decompose our wedges into a
portion that comes from explicit taxes imposed by governments and a portion
that comes from frictions in detailed models. This decomposition would be
particularly useful when explicit taxes vary significantly over the business
cycle.

Researchers have argued---quite beyond the prominent model of Bernanke and
Gertler (1989)---that frictions in financial markets are important for
business cycle fluctuations. (See Bernanke (1983) and the motivation in
Bernanke and Gertler (1989).) We stress that our findings do not contradict
this idea. Indeed, we have shown that a detailed economy with
input-financing frictions is equivalent to a prototype economy with
efficiency wedges. In this sense, while existing models of financial
frictions are not promising, new models in which financial frictions show up
as efficiency and labor wedges are.

Our results suggest that future theoretical work should focus on developing
models which lead to fluctuations in efficiency and labor wedges. Many
existing models produce fluctuations in labor wedges. The challenging task
is to develop detailed models in which primitive shocks lead to fluctuations
in efficiency wedges as well.

\bigskip

\noindent \emph{University of Minnesota and Research Department, Federal
Reserve Bank of Minneapolis, 90 Hennepin Avenue, Minneapolis, MN 55401,
U.S.A.; chari@res.mpls.frb.fed.us}

\begin{center}
and
\end{center}

\emph{Research Department, Federal Reserve Bank of Minneapolis, 90 Hennepin
Avenue, Minneapolis, MN 55401, U.S.A., and University of Minnesota;
pkehoe@res.mpls.frb.fed.us}

\begin{center}
and
\end{center}

\emph{Research Department, Federal Reserve Bank of Minneapolis, 90 Hennepin
Avenue, Minneapolis, MN 55401, U.S.A., and University of Minnesota;
erm@mcgrattan.mpls.frb.fed.us}

\bigskip \newpage

%TCIMACRO{%
%\TeXButton{TeX field}{\renewcommand{\baselinestretch}{1.0}\normalsize}}%
%BeginExpansion
\renewcommand{\baselinestretch}{1.0}\normalsize%
%EndExpansion

\begin{center}
\textbf{APPENDIX: The Mapping for Two Other Wedges}
\end{center}

Here we demonstrate the mapping from two other detailed economies with
frictions to two prototype economies with wedges. In the preceding text, we
have described the mapping for efficiency and labor wedges. In this
appendix, we describe it for investment and government consumption wedges.

\bigskip

\begin{center}
\textbf{A. Investment Wedges Due to Financial Frictions}
\end{center}

We start with the mapping of financial frictions to investment wedges.

In Chari, Kehoe, and McGrattan (2004), we show the equivalence between the
Carlstrom and Fuerst (1997) model and a prototype economy. Here we focus on
the financial frictions in the Bernanke, Gertler, and Gilchrist (1999) model
and abstract from the monetary features of that model. Bernanke, Gertler,
and Gilchrist begin by deriving the optimal financial contracts between
risk-neutral entrepreneurs and financial intermediaries in an environment
with no aggregate uncertainty. These contracts resemble debt contracts (with
default). Bernanke, Gertler, and Gilchrist try to extend their derivation of
optimal contracts to an economy with aggregate uncertainty. The contracts
they consider are not optimal given the environment, because these contracts
do not allow risk sharing between risk-averse consumers and risk-neutral
entrepreneurs. Here we solve for optimal debt-like contracts that
arbitrarily rule out such risk sharing, but even so, our first-order
conditions differ from those of Bernanke, Gertler, and Gilchrist. (One
reason for this difference is that our break-even constraint for the
financial intermediary and our law of motion for entrepreneurial net worth
differ from theirs. See equations (\ref{breakeven}) and (\ref{n})\ below.)

\bigskip

\noindent a. \emph{A Detailed Economy With Financial Frictions}

The Bernanke-Gertler-Gilchrist model has a continuum of risk-neutral
entrepreneurs of mass $L_{e}$, a continuum of consumers of mass 1, and a
representative firm. Output $y(s^{t})$ is produced according to 
\begin{equation}
y(s^{t})=A(s^{t})k^{\alpha }\left[ l^{\Omega }L_{e}^{1-\Omega }\right]
^{1-\alpha },  \label{bggprodn}
\end{equation}%
where $A(s^{t}),k,$ and $l$ are the technology shock, the capital stock, and
the labor supplied by consumers. The stochastic process for the technology
shock is given by $\log A(s^{t+1})=(1-\rho _{A})\log A+\rho _{A}\log
A(s^{t})+\varepsilon _{A}(s^{t+1}).$ Each entrepreneur supplies one unit of
labor inelastically. The representative firm's maximization problem is to
choose $l,L_{e},k$ to maximize profits $A(s^{t})k^{\alpha }\left[ l^{\Omega
}L_{e}^{1-\Omega }\right] ^{1-\alpha }-w(s^{t})l-w_{e}(s^{t})L_{e}-r(s^{t})k$%
, where $w(s^{t}),$ $w_{e}(s^{t}),$ and $r(s^{t})$ denote the wage rate for
consumers, the wage rate for entrepreneurs, and the rental rate on capital.

New capital goods can be produced only by entrepreneurs. Each entrepreneur
owns a technology that transforms output and old capital at the end of any
period into capital goods at the beginning of the following period. In each
period $t,$ each entrepreneur receives an idiosyncratic shock $\omega $
drawn from a distribution $F(\omega )$ with expected value 1. This shock is
i.i.d. across entrepreneurs and time. The realization of $\omega $ is
private information to the entrepreneur. An entrepreneur who buys $%
k(s^{t-1}) $ units of goods in period $t-1$ produces $\omega k(s^{t-1})$
units of capital at the beginning of period $t.$ These capital goods are
sold at price $R_{k}(s^{t})=r(s^{t})+(1-\delta )$, where $\delta $ is the
rate of depreciation of the capital goods.

Entrepreneurs finance the production of new capital goods partly with their
own net worth, $n(s^{t-1}),$ and partly with loans from financial
intermediaries. These intermediaries offer contracts with the following
cutoff form: in all idiosyncratic states at $t$ in which $\omega \geq \bar{%
\omega}(s^{t})$, the entrepreneur pays $\bar{\omega}%
(s^{t})R_{k}(s^{t})k(s^{t-1})$ and keeps $[\omega -\bar{\omega}%
(s^{t})]R_{k}(s^{t})k(s^{t-1}).$ In all other states, the entrepreneur
receives nothing while the financial intermediary receives $\omega
R_{k}(s^{t})k(s^{t-1})$ net of monitoring costs $\mu \omega
R_{k}(s^{t})k(s^{t-1}).$ We assume that financial intermediaries make zero
profits in equilibrium.

Given an entrepreneur's net worth $n(s^{t-1}),$ the contracting problem for
a representative entrepreneur is to choose the cutoff $\bar{\omega}(s^{t})$
for each state and the amount of goods invested $k(s^{t-1})$ to maximize the
expected utility of the entrepreneurs, 
\[
\sum \pi (s^{t}|s^{t-1})\text{{\large \{[}}(1-\Gamma \text{{\large (}}\bar{%
\omega}(s^{t})\text{{\large )]}}R_{k}(s^{t})k(s^{t-1})~dF(\omega )\text{%
{\large \}}}, 
\]
subject to a break-even constraint for the intermediary, 
\begin{equation}
\sum (s^{t}|s^{t-1})\text{{\large [}}\Gamma \text{{\large (}}\bar{\omega}%
(s^{t})\text{{\large )}}-\mu G\text{{\large (}}\bar{\omega}(s^{t})\text{%
{\large )]}}R_{k}(s^{t})k(s^{t-1})=k(s^{t-1})-n(s^{t-1}),  \label{breakeven}
\end{equation}
where $\Gamma (\bar{\omega})=\int_{0}^{\bar{\omega}}\omega f(\omega
)~d\omega +\bar{\omega}\int_{\bar{\omega}}^{\infty }f(\omega )~d\omega $ and 
$G(\bar{\omega})=\int_{0}^{\bar{\omega}}\omega f(\omega )~d\omega .$ Here $%
q(s^{t}|s^{t-1})$ denotes the price of consumption goods in state $s^{t}$ in
units of consumption goods in state $s^{t-1}.$

This formulation implies an aggregation result: The capital demand of the
entrepreneurs is linear in their net worth, so that total demand for goods
from them depends only on their total net worth. The solution to the
contracting problem is characterized by the first-order conditions with
respect to $k(s^{t-1})$ and $\bar{\omega}(s^{t})$, which can summarized by 
\begin{equation}
\frac{\sum \pi (s^{t}|s^{t-1})\text{{\large [}}1-\Gamma \text{{\large (}}%
\bar{\omega}(s^{t})\text{{\large )]}}R_{k}(s^{t})}{\sum \pi
(s^{t}|s^{t-1})\Gamma ^{\prime }\text{{\large (}}\bar{\omega}(s^{t})\text{%
{\large )}}R_{k}(s^{t})}=\frac{\sum q(s^{t}|s^{t-1})\text{{\large [}}\Gamma 
\text{{\large (}}\bar{\omega}(s^{t})\text{{\large )}}-\mu G\text{{\large (}}%
\bar{\omega}(s^{t})\text{{\large )]}}R_{k}(s^{t})-1}{\sum q(s^{t}|s^{t-1})%
\text{{\large [}}\Gamma ^{\prime }\text{{\large (}}\bar{\omega}(s^{t})\text{%
{\large )}}-\mu G^{\prime }\text{{\large (}}\bar{\omega}(s^{t})\text{{\large %
)]}}R_{k}(s^{t})}  \label{OmegaBar}
\end{equation}
and the break-even constraint (\ref{breakeven}).

In each period, a fraction $\gamma $ of existing entrepreneurs dies and is
replaced by a fraction $\gamma $ of newborn entrepreneurs. At the beginning
of each period, entrepreneurs learn whether they will die this period. We
assume that $\gamma $ is sufficiently small and the technology for producing
investment goods is sufficiently productive so that entrepreneurs consume
their net worth only when they are about to die. All entrepreneurs who are
going to die consume their entire net worth and do not supply labor in the
current period. (The newborn replacements do instead.) Those entrepreneurs
who do not die save their wage income plus their income from producing
capital goods. The aggregate income of the entrepreneurs is, then, 
\[
\int \left[ \omega -\bar{\omega}(s^{t})\right] R_{k}(s^{t})k(s^{t-1})~dF(%
\omega )+w_{e}(s^{t})L_{e}, 
\]
where $k(s^{t-1})$ is the aggregate capital stock. The law of motion for
aggregate net worth is given by

\begin{equation}
n(s^{t})=\gamma \int \left[ \omega -\bar{\omega}(s^{t})\right]
R_{k}(s^{t})k(s^{t-1})~dF(\omega )+w_{e}(s^{t})L_{e}.  \label{n}
\end{equation}
Total consumption by entrepreneurs in any period is 
\begin{equation}
c_{e}(s^{t})=(1-\gamma )\int \left[ \omega -\bar{\omega}(s^{t})\right]
R_{k}(s^{t})k(s^{t-1})~dF(\omega ).  \label{ce}
\end{equation}

Consumers maximize utility given by 
\begin{equation}
\sum_{t=0}^{\infty }\sum_{s^{t}}\,\beta ^{t}\pi _{t}(s^{t})\,U\text{{\large (%
}}c(s^{t}),l(s^{t})\text{{\large )}},  \label{utility}
\end{equation}%
where $c(s^{t})$ denotes consumption in state $s^{t}$ subject to 
\begin{equation}
c(s^{t})+\sum_{s_{t+1}}q(s^{t+1}|s^{t})b(s^{t+1})\leq
w(s^{t})l(s^{t})+b(s^{t})+T(s^{t}),  \nonumber
\end{equation}%
for $t=0,1,\ldots ,$ and borrowing constraints, $b(s^{t+1})\geq $ $\bar{b},$
for some large negative number $\bar{b}.$ Here $T(s^{t})$ is lump-sum
transfers. The initial condition $b(s^{0})$ is given. Each of the bonds $%
b(s^{t+1})$ is a claim to one unit of consumption in state $s^{t+1}$ and
costs $q(s^{t+1}|s^{t})$ dollars in state $s^{t}.$ The first-order
conditions for the consumer can be written as 
\begin{eqnarray}
-\frac{U_{l}(s^{t})}{U_{c}(s^{t})} &=&w(s^{t})\text{ and}
\label{Euler for money} \\
q(s^{t+1}|s^{t}) &=&\beta \pi (s^{t+1}|s^{t})\frac{U_{c}(s^{t+1})}{%
U_{c}(s^{t})}.  \label{interest rate}
\end{eqnarray}

The market-clearing condition for final goods is then 
\[
c(s^{t})+c_{e}(s^{t})+\mu G\text{{\large (}}\bar{\omega}(s^{t})\text{{\large %
)}}R_{k}(s^{t})k(s^{t-1})+k(s^{t})-(1-\delta )k(s^{t-1})=y(s^{t}). 
\]

\bigskip

\noindent b. \emph{The Associated Prototype Economy With Investment Wedges}

Now consider a prototype economy which is the same as our benchmark
prototype economy, except for the following changes. We assume that the
production function is as in (\ref{bggprodn}), with $L_{e}$ interpreted as a
fixed input rented from the government, and we assume that consumers are
taxed on capital income but not on investment or labor income. With capital
income taxes, the consumers' budget constraint is given by 
\[
c(s^{t})+k(s^{t})-(1-\delta )k(s^{t-1})=w(s^{t})l(s^{t})+[1-\tau
_{k}(s^{t})]r(s^{t})k(s^{t-1})+\delta \tau _{k}(s^{t})k(s^{t-1})+T(s^{t}), 
\]%
where $\tau _{k}(s^{t})$ is the tax rate on capital income. Here $\tau
_{k}(s^{t})$ plays the role of an investment wedge. The resource constraint
for the prototype economy is as in the benchmark prototype economy. Let
government consumption in the prototype economy be given by 
\begin{equation}
g(s^{t})=c_{e}^{\ast }(s^{t})+\mu G\text{{\large (}}\bar{\omega}^{\ast
}(s^{t})\text{{\large )}}R_{k}^{\ast }(s^{t})k^{\ast }(s^{t-1}),
\label{gbgg}
\end{equation}%
where asterisks denote the allocations in the detailed economy with
investment frictions.

We now show how the tax on capital income in our prototype economy can be
constructed from the detailed economy. First, the break-even constraint in
the detailed economy can be rewritten as 
\[
\sum q^{\ast }(s^{t}|s^{t-1})\left\{ \text{{\large [}}\Gamma \text{{\large (}%
}\bar{\omega}^{\ast }(s^{t})\text{{\large )}}-\mu G\text{{\large (}}\bar{%
\omega}^{\ast }(s^{t})\text{{\large )]}}R_{k}^{\ast }(s^{t})+\frac{n^{\ast
}(s^{t-1})}{k^{\ast }(s^{t-1})}\frac{U_{c}^{\ast }(s^{t-1})}{\beta \pi
(s^{t}|s^{t-1})U_{c}^{\ast }(s^{t})}\right\} =1, 
\]
where $q^{\ast }(s^{t}|s^{t-1})=\beta \pi (s^{t}|s^{t-1})U_{c}^{\ast
}(s^{t})/U_{c}^{\ast }(s^{t-1}).$ The intertemporal Euler equation in the
prototype economy is

\[
\sum q(s^{t}|s^{t-1})\text{{\large \{[}}(1-\tau _{k}(s^{t})\text{{\large ]}}%
A(s^{t})F_{k}(s^{t})+(1-\delta )\text{{\large \}}}=1, 
\]%
where $q(s^{t}|s^{t-1})=\beta \pi
(s^{t}|s^{t-1})U_{c}(s^{t})/U_{c}(s^{t-1}). $ Let the tax rate on capital
income $\tau _{k}(s^{t})$ be such that 
\begin{eqnarray}
&&[1-\tau _{k}(s^{t})][A(s^{t})F_{k}^{\ast }(s^{t})-\delta ]+1
\label{bggeuler} \\
&=&\text{{\large [}}\Gamma \text{{\large (}}\bar{\omega}^{\ast }(s^{t})\text{%
{\large )}}-\mu G\text{{\large (}}\bar{\omega}^{\ast }(s^{t})\text{{\large )]%
}}R_{k}^{\ast }(s^{t})+\frac{n^{\ast }(s^{t-1})}{k^{\ast }(s^{t-1})}\frac{%
U_{c}^{\ast }(s^{t-1})}{\beta \pi (s^{t}|s^{t-1})U_{c}^{\ast }(s^{t})}. 
\nonumber
\end{eqnarray}%
Comparing first-order conditions for the two economies, we then have this
proposition:

\bigskip

\textsc{Proposition }6:\emph{\ Consider the prototype economy just
described, with government consumption given by }(\ref{gbgg})\emph{\ and
capital income taxes }$\emph{by}$\emph{\ }(\ref{bggeuler})\emph{. The
aggregate equilibrium allocations for this prototype economy coincide with
those of the detailed economy with financial frictions}$.$

\bigskip

\begin{center}
\textbf{B. Government Consumption Wedges Due to International Borrowing and
Lending}
\end{center}

Now we develop a detailed economy with international borrowing and lending
and show that net exports in that economy are equivalent to a government
consumption wedge in an associated prototype economy.

\bigskip

\noindent a. \emph{A Detailed Economy With International Borrowing and
Lending}

Consider a model of a world economy with $N$ countries and a single
homogenous good in each period. We use the same notation for uncertainty as
before.

The representative consumer in country $i$ has preferences 
\begin{equation}
\sum \beta ^{t}\pi _{t}(s^{t})U\text{{\large (}}c_{i}(s^{t}),l_{i}(s^{t})%
\text{{\large )}},  \label{preferences 2}
\end{equation}%
where $c_{i}(s^{t})$ and $l_{i}(s^{t})$ denote consumption and labor. The
consumer's budget constraint is 
\begin{equation}
c_{i}(s^{t})+b_{i}(s^{t})+k_{i}(s^{t})\leq F\text{{\large (}}%
k_{i}(s^{t-1}),l_{i}(s^{t})\text{{\large )}}+(1-\delta
)k_{i}(s^{t-1})+\sum_{s^{t+1}}q(s^{t+1}/s^{t})b_{i}(s^{t+1}),  \label{16}
\end{equation}%
where $b^{i}(s^{t+1})$ denotes the amount of state-contingent borrowing by
the consumer in country $i$ in period $t$, $q(s^{t+1}/s^{t})$ denotes the
corresponding state-contingent price, and $k_{i}(s^{t})$ denotes the capital
stock.

An \textit{equilibrium for this detailed economy} is a set of allocations 
{\large (}$c_{i}(s^{t}),k_{i}(s^{t}),l_{i}(s^{t}),$\linebreak $%
b_{i}(s^{t+1}) ${\large )} and prices $q(s^{t}/s^{t-1})${\large \ }such that
these allocations both solve the consumer's problem in each country $i$ and
satisfy the world resource constraint: 
\begin{equation}
\sum_{i=1}^{N}[c_{i}(s^{t})+k_{i}(s^{t})]\leq \sum_{i=1}^{N}\text{{\large [}}%
F\text{{\large (}}k_{i}(s^{t-1}),l_{i}(s^{t})\text{{\large )}}+(1-\delta
)k_{i}(s^{t-1})\text{{\large ].}}  \label{world resource}
\end{equation}%
Note that in this economy, the net exports of country $i$ are given by 
\[
F\text{{\large (}}k_{i}(s^{t-1}),l_{i}(s^{t})\text{{\large )}}%
-[k_{i}(s^{t})-(1-\delta )k_{i}(s^{t-1})]-c_{i}(s^{t}). 
\]

\bigskip

\noindent b. \emph{The Associated Prototype Economy With Government
Consumption Wedges}

Now consider a prototype economy of a single closed economy $i$ with an
exogenous stochastic variable, government consumption\textit{\ }$%
g_{i}(s^{t}),$ which we call the \textit{government consumption wedge}. In
this economy, consumers maximize (\ref{preferences 2}) subject to their
budget constraint 
\begin{equation}
c_{i}(s^{t})+k_{i}(s^{t})=w_{i}(s^{t})l_{i}(s^{t})+\left[ r_{i}(s^{t})+1-%
\delta \right] k_{i}(s^{t-1})+T_{i}(s^{t}),  \label{prototype budget}
\end{equation}%
where $w_{i}(s^{t}),$ $r_{i}(s^{t}),$ and $T_{i}(s^{t})$ are the wage rate,
the capital rental rate, and lump-sum transfers. In each state $s^{t},$
firms choose $k$ and $l$ to maximize $F(k,l)-r_{i}(s^{t})k-w_{i}(s^{t})l$.
The government's budget constraint is 
\begin{equation}
g_{i}(s^{t})+T_{i}(s^{t})=0.  \label{government budget}
\end{equation}%
The resource constraint for this economy is 
\begin{equation}
c_{i}(s^{t})+g_{i}(s^{t})+k_{i}(s^{t})=F\text{{\large (}}%
k_{i}(s^{t-1}),l_{i}(s^{t})\text{{\large )}}+(1-\delta )k_{i}(s^{t-1}).
\label{resource 2}
\end{equation}%
An \textit{equilibrium of the prototype economy} is, then, a set of
allocations {\large (}$c_{i}(s^{t}),k_{i}(s^{t}),l_{i}(s^{t}),g_{i}(s^{t}),%
\linebreak T_{i}(s^{t})${\large )} and prices {\large (}$%
w_{i}(s^{t}),r_{i}(s^{t})${\large )} such that these allocations are optimal
for consumers and firms and the resource constraint is satisfied.

The following proposition shows that the government consumption wedge in
this prototype economy consists of net exports in the original economy.

\bigskip

\textsc{Proposition }7:\textit{\ }\emph{Consider the equilibrium allocations}
{\large (}$c_{i}^{\ast }(s^{t}),k_{i}^{\ast }(s^{t}),l_{i}^{\ast
}(s^{t}),b_{i}^{\ast }(s^{t+1})${\large )} \emph{for country }$i$\emph{\ in
the detailed economy. Let the government consumption wedge be} 
\begin{equation}
g_{i}(s^{t})=F\text{{\large (}}k_{i}^{\ast }(s^{t-1}),l_{i}^{\ast }(s^{t})%
\text{{\large )}}-\left[ k_{i}^{\ast }(s^{t})-(1-\delta )k_{i}^{\ast
}(s^{t-1})\right] -c_{i}^{\ast }(s^{t}),  \label{g}
\end{equation}%
\emph{let the wage and capital rental rates be }$w_{i}(s^{t})=F_{li}^{\ast
}(s^{t})$ \emph{and} $r_{i}(s^{t})=F_{ki}^{\ast }(s^{t}),$ \emph{and let} $%
T_{i}(s^{t})$ \emph{be defined by }(\ref{government budget}). \emph{Then the
allocations} {\large (}$c_{i}^{\ast }(s^{t}),k_{i}^{\ast
}(s^{t}),l_{i}^{\ast }(s^{t}),g_{i}^{\ast }(s^{t}),T_{i}(s^{t})${\large )} 
\emph{and the prices }{\large (}$w_{i}(s^{t}),r_{i}(s^{t})${\large )}\emph{\
are an equilibrium for the prototype economy.} \bigskip

The proof follows by noting that the first-order conditions are the same in
the two economies and that, given the government consumption wedge (\ref{g}%
), the consumer's budget constraint (\ref{16}) in the detailed economy is
equivalent to the resource constraint (\ref{resource 2}) in the prototype
economy.

Note that for simplicity we have abstracted from government consumption in
the detailed economy. If that economy had government consumption as well,
then the government consumption wedge in the prototype economy would be the
sum of net exports and government consumption in the detailed
economy.\newpage

%TCIMACRO{%
%\TeXButton{TeX field}{\renewcommand{\baselinestretch}{1.5}\normalsize}}%
%BeginExpansion
\renewcommand{\baselinestretch}{1.5}\normalsize%
%EndExpansion

\begin{center}
\textbf{\large REFERENCES}
\end{center}

\textsc{Bernanke, B.} (1983): \textquotedblleft Nonmonetary Effects of the
Financial Crisis in the Propagation of the Great
Depression,\textquotedblright\ \emph{American Economic Review,} 73, 257--276.

\textsc{Bernanke, B., and M. Gertler} (1989): \textquotedblleft Agency
Costs, Net Worth, and Business Fluctuations,\textquotedblright\ \textit{%
American Economic Review}, 79, 14--31.

\textsc{Bernanke, B., M. Gertler, and S. Gilchrist} (1999):
\textquotedblleft The Financial Accelerator in a Quantitative Business Cycle
Framework,\textquotedblright\ in \textit{Handbook of Macroeconomics,} Volume
1C, ed. by J. Taylor and M. Woodford. Amsterdam: North-Holland.

\textsc{Bordo, M., C. Erceg, and C. Evans} (2000): \textquotedblleft Money,
Sticky Wages, and the Great Depression,\textquotedblright\ \textit{American
Economic Review,} 90, 1447--1463.

\textsc{Braun, R.} (1994): \textquotedblleft How Large Is the Optimal
Inflation Tax?\textquotedblright\ \textit{Journal of Monetary} \textit{%
Economics,} 34, 201--214.

\textsc{Carlstrom, C., and T. Fuerst} (1997): \textquotedblleft Agency
Costs, Net Worth, and Business Fluctuations: A Computable General
Equilibrium Analysis,\textquotedblright\ \textit{American Economic\ Review,}
87, 893--910.

\textsc{Chari, V., P. Kehoe, and E. McGrattan} (2002): \textquotedblleft
Accounting for the Great Depression,\textquotedblright\ \textit{American
Economic Review}, 92, 22--27.

%TCIMACRO{\TeXButton{rule}{\rule[-0.02in]{0.81in}{0.2pt}} }%
%BeginExpansion
\rule[-0.02in]{0.81in}{0.2pt}
%EndExpansion
(2004): \textquotedblleft Business Cycle Accounting,\textquotedblright\
Working Paper 10351, National Bureau of Economic Research.

%TCIMACRO{\TeXButton{rule}{\rule[-0.02in]{0.81in}{0.2pt}} }%
%BeginExpansion
\rule[-0.02in]{0.81in}{0.2pt}
%EndExpansion
(2005): \textquotedblleft A Critique of Structural VARs Using Business Cycle
Theory,\textquotedblright\ Research Department Staff Report 364, Federal
Reserve Bank of Minneapolis.

%TCIMACRO{\TeXButton{rule}{\rule[-0.02in]{0.81in}{0.2pt}} }%
%BeginExpansion
\rule[-0.02in]{0.81in}{0.2pt}
%EndExpansion
(2006): \textquotedblleft Appendices: Business Cycle
Accounting,\textquotedblright\ Research Department Staff Report 362, Federal
Reserve Bank of Minneapolis.

\textsc{Christiano, L., C. Gust, and J. Roldos} (2004): \textquotedblleft
Monetary Policy in a Financial Crisis,\textquotedblright\ \emph{Journal of
Economic Theory,} 119, 64--103.

\textsc{Chu, T.} (2001): \textquotedblleft Exit Barriers and Economic
Stagnation: The Macro-impact of Government Subsidies to
Industries,\textquotedblright\ Manuscript, East-West Center.

\textsc{Cole, H., and L. Ohanian} (1999): \textquotedblleft The Great
Depression in the United States from a Neoclassical
Perspective,\textquotedblright\ \textit{Federal Reserve Bank of Minneapolis
Quarterly Review}, 23(Winter), 2--24.

%TCIMACRO{\TeXButton{rule}{\rule[-0.02in]{0.81in}{0.2pt}} }%
%BeginExpansion
\rule[-0.02in]{0.81in}{0.2pt}
%EndExpansion
(2002): \textquotedblleft The U.S. and U.K. Great Depressions through the
Lens of Neoclassical Growth Theory,\textquotedblright\ \textit{American
Economic Review,} 92, 28--32.

%TCIMACRO{\TeXButton{rule}{\rule[-0.02in]{0.81in}{0.2pt}} }%
%BeginExpansion
\rule[-0.02in]{0.81in}{0.2pt}
%EndExpansion
(2004): \textquotedblleft New Deal Policies and the Persistence of the Great
Depression: A General Equilibrium Analysis,\textquotedblright\ \textit{%
Journal of Political Economy}, 112, 779--816.

\textsc{Cooley, T.,}\ ed. (1995): \textit{Frontiers of Business Cycle
Research}. Princeton: Princeton University Press.

\textsc{Cooper, R., and J. Ejarque} (2000): \textquotedblleft Financial
Intermediation and Aggregate Fluctuations: A Quantitative
Analysis,\textquotedblright\ \ \textit{Macroeconomic Dynamics}, 4(4),
423--447.

\textsc{Doms, M., and T. Dunne }(1994): \textquotedblleft Capital Adjustment
Patterns in Manufacturing Plants\textquotedblright\ CES 94-11, U.S. Bureau
of the Census.

\textsc{Gali, J., M. Gertler, and D. Lopez-Salido}\ (forthcoming):
\textquotedblleft Markups, Gaps, and the Welfare Costs of Business
Fluctuations,\textquotedblright\ \emph{Review of Economics and Statistics}.

\textsc{Hall, R.} (1997): \textquotedblleft Macroeconomic Fluctuations and
the Allocation of Time,\textquotedblright\ \textit{Journal} \textit{of Labor
Economics,} 15(Part 2), S223--S250.

\textsc{Hornstein, A., and E. Prescott} (1993): \textquotedblleft The Firm
and the Plant in General Equilibrium Theory,\textquotedblright\ in \textit{%
General Equilibrium, Growth, and Trade, Vol. 2: The Legacy of Lionel McKenzie%
}, ed. by R. Becker et al. San Diego: Academic Press.

\textsc{Ingram, B., N. Kocherlakota, and N. Savin}\ (1997):
\textquotedblleft Using Theory for Measurement: An Analysis of the Cyclical
Behavior of Home Production,\textquotedblright\ \textit{Journal of Monetary
Economics}, 40, 435--456.

\textsc{Kehoe, T., and E. Prescott} (2002): \textquotedblleft Great
Depressions of the 20th Century,\textquotedblright\ \textit{Review of
Economic Dynamics}, 5, 1--18.

\textsc{Kiyotaki, N., and J. Moore} (1997): \textquotedblleft Credit
Cycles,\textquotedblright\ \textit{Journal of Political Economy}, 105,
211--248.

\textsc{Kydland, F., and E. Prescott} (1982): "Time to Build and Aggregate
Fluctuations,\textquotedblright\ \textit{Econometrica}, 50, 1345--1370.

%TCIMACRO{\TeXButton{rule}{\rule[-0.02in]{0.81in}{0.2pt}} }%
%BeginExpansion
\rule[-0.02in]{0.81in}{0.2pt}
%EndExpansion
(1988): \textquotedblleft The Workweek of Capital and Its Cyclical
Implications,\textquotedblright\ \textit{Journal of Monetary Economics}, 21,
343--360.

\textsc{Lagos, R.} (2006): \textquotedblleft A Model of
TFP,\textquotedblright\ \emph{Review of Economic Studies}, 73, 983--1007.

\textsc{McGrattan, E.} (1991): \textquotedblleft The Macroeconomic Effects
of Distortionary Taxation,\textquotedblright\ Institute for Empirical
Macroeconomics Discussion Paper 37, Federal Reserve Bank of Minneapolis.

\textsc{Mulligan, C.}\ (2002a): \textquotedblleft A Century of Labor-Leisure
Distortions,\textquotedblright\ Working Paper 8774, National Bureau of
Economic Research.

%TCIMACRO{\TeXButton{rule}{\rule[-0.02in]{0.81in}{0.2pt}}}%
%BeginExpansion
\rule[-0.02in]{0.81in}{0.2pt}%
%EndExpansion
\textbf{\ }(2002b): \textquotedblleft A Dual Method of Empirically
Evaluating Dynamic Competitive Equilibrium Models with Market Distortions,
Applied to the Great Depression and World War II,\textquotedblright\ Working
Paper 8775, National Bureau of Economic Research.

\textsc{Parkin, M.} (1988): \textquotedblleft A Method for Determining
Whether Parameters in Aggregative Models Are Structural,\textquotedblright\ 
\textit{Carnegie-Rochester Conference Series on Public Policy}, 29, 215--252.

\textsc{Prescott, E.} (1986): \textquotedblleft Theory Ahead of Business
Cycle Measurement,\textquotedblright\ \textit{Federal} \textit{Reserve Bank
of Minneapolis Quarterly Review}, 10(Fall), 9--22.

%TCIMACRO{\TeXButton{rule}{\rule[-0.02in]{0.81in}{0.2pt}} }%
%BeginExpansion
\rule[-0.02in]{0.81in}{0.2pt}
%EndExpansion
(1999): \textquotedblleft Some Observations on the Great
Depression,\textquotedblright\ \textit{Federal Reserve} \textit{Bank of
Minneapolis Quarterly Review}, 23(Winter), 25--31.

\textsc{Restuccia, D., and R. Rogerson} (2003): \textquotedblleft Policy
Distortions and Aggregate Productivity with Heterogeneous
Plants,\textquotedblright\ Manuscript, Arizona State University.

\textsc{Rotemberg, J., and M. Woodford} (1991): \textquotedblleft Markups
and the Business Cycle,\textquotedblright\ in \textit{NBER Macroeconomics
Annual 1991,} ed. by O. Blanchard and S. Fischer. Cambridge, Mass.: MIT\
Press.

%TCIMACRO{\TeXButton{rule}{\rule[-0.02in]{0.81in}{0.2pt}} }%
%BeginExpansion
\rule[-0.02in]{0.81in}{0.2pt}
%EndExpansion
(1999): \textquotedblleft The Cyclical Behavior of Prices and
Costs,\textquotedblright\ in \textit{Handbook of Macroeconomics,} ed. by J.
Taylor and M. Woodford.\textit{\ }Amsterdam: North-Holland.

\textsc{Schmitz, J.}\ (2005): \textquotedblleft What Determines Labor
Productivity? Lessons From the Dramatic Recovery of the U.S. and Canadian
Iron-Ore Industries Following Their Early 1980s Crisis,\textquotedblright\ 
\emph{Journal of Political Economy,} 113, 582--625.

\newpage \begingroup\setlength{\parindent}{0pt}\setlength{\parskip}{0ex}%
\renewcommand{\enotesize}{\normalsize}\theendnotes\endgroup

\end{document}
